\subsection{Agendas}\label{agendas}

There's a specific fetus agenda lifetime to lifetime. The \emph{avatar}
agenda evolves the greater soul's ability to generate light and have
experiences over thousands and thousands of \emph{I am} expressions who
have been fetuses. There are times where the over-soul --- the avatar
--- gets looped in servitude to a system which lowers its capacity to
use light, and, as a result, it cannot expand.

A non-agenda being occurs when time is irrelevant to the great
experience. Linear time is not the focus of the agenda. It may do one
thing twenty-eight thousand years ago, seventeen things two years ago,
two million things forty-eight million years ago, and that, technically
speaking, is a non-agenda. The things done in the non-agenda create a
resolution for some agendas or apply potential solutions for agendas
stuck and unable move forward. Non-agenda allows us to cut and paste
time-based experiences out of certain \emph{I am} experiences and use
them temporarily in a new \emph{I am} expression to manifest past or
future non-agenda aspects into a present agenda.

\subsection{The Awakening Journey}\label{the-awakening-journey}

We live on a seventh dimensional seed planet. Earth can teleport itself
through time and space seed worlds. These worlds are a blank sheet. They
have no akashic record. The life force seeded by earth allows the new
world to start growing with its own akashic record.

When we reconnect with source, we become celestial mediums of peace. We
start using the womb chakras to create. This was earth's original plan.
This planet seeds life and brings the celestial minds into the planet to
bond within the solar system. THE celestial mind extends spiritual
contracts to a sun. The sun extends its contracts to the life force.
This connects it to the Galactic Celestial Commerce Market.

Awakening is kindling of the awareness strand of galactic commerce
through celestial minds, using celestial mediums as the guides and
guideposts of the many frequencies of time. This allows the ocean of
awareness to go into the sea of consciousness and generate incarnations
and reincarnations within a solar system. A solar system is an energetic
or a physical being within a world, there to experience the strands of
connectivity.

The earth was originally created for the unique experience of spawning
new galaxies. That was the design and intent. The opposite has occurred.
The earth was heavily manipulated into becoming a DNA farm by means of
the time travel wars. Source connection became the greater mission. Our
sound and light fractal, our dimension, was hacked. We were set upon the
worship of false gods. The misdirection or harvesting of human
intentional energy is the basis of false fractals of the divine
hologram. It's a multidimensional expression of building our own prison.
We are co-creators. Even if we've forgotten that, they haven't.

Our mission is to experience the infinite ways soul connects and
disconnects from source. Earth offers a vast variety of messages and
concepts to learn soul disconnection. As we disentangle from the system
of domination and control, from past lives gone awry, the more we can
step into the understanding of true soul connection. There are people on
earth who planned hundreds of lives in advance to be here now to assist
with this process. We can call this the resistance of free earth.
They're here to find the soul codes among all of our species and
complete them. Domination and control could no longer keep us separate
as soul families with a complete soul code.

\subsection{Celestial Medium Journey}\label{celestial-medium-journey}

The journey to celestial medium begins with self-mastery by daily
practice, which becomes a monthly practice, a yearly practice, then a
constant practice, a function as ingrained as breathing. A celestial
medium expands consciousness to become a translator of the \emph{blue
road of spirit}, knowledge of the spirit and the ancestry working with
you.

Mastering the finite \emph{I am} while acknowledging the infinite
\emph{I am} creates the medium space by which consciousness skirts the
sides of infinite and finite. The celestial medium takes up the million
letter alphabet in this space, compresses it with their precognitive
workforce, and uploads to the implicate \emph{I am}. The explicate
\emph{I am} --- the incarnation --- consciously downloads it to process
and manifest. It then returns the data back to the implicate \emph{I am}
--- the being in the sea of consciousness within the ocean of awareness
--- uploading back to the universe. The human mind and body can't hold
the information forever. This is the back and forth method between the
implicate and explicate \emph{I am} through the process of the celestial
medium.

There is a receive, respond, retain, release process in passing higher
frequency information from the body's perspective. Bring it into the
body. Unpack it. Decode it. This avails the data to your higher
frequency level. The packed information goes up to the crown chakra and
back to the original source --- the frequency pattern of the universe
around us.

We are incarnate life forms here now. We are not up there in the
celestial realms. It creates distortion in us if we hold on to it. Many
channelers end up corrupt because they don't let go of the information.
They hoard it. The distortions lie unconsciousness in their bodies. It
can lead to possession. There are external sources that want to possess
bodies hoarding information. They dissolve the information into pure
energy and feed on it. Letting go of that information is one-hundred
percent conscious effort. We must say, I am packing this information
back up, knowing full well that I cannot hold on to it, and then release
it back to the universe.

Our bodies adapt and evolve in this celestial medium process. We can't
really say we're both --- an incarnate life form and a non \emph{I am}
on the celestial medium side, which perceives time in a much longer
length. Whatever agenda the micro-soul has. it's dwarfed compared to the
celestial medium's length of time. The agendas don't match through
length of time, but they are both in equal experience simultaneously.
You experience the super long game of the celestial mind, and the long
game of the \emph{I am}. It works with the higher spirit to be in the
medium space. From the medium space it transfers the \emph{allness} of
the \emph{I am} into the code, downloads the code, returns to the
\emph{I am} state, manifests with the code, then puts the code back into
the celestial space. We simultaneously experience local time to super
long galactic time, going back and forth, the finite and infinite
\emph{I am} equally and continuously changing frequency without
competition for temporal dominance.

A self-spawned celestial medium is a planet's translator, able to speak
to and communicate with other celestial minds, and it translates from
the higher frequency to the lower density energy, allowing everyone to
understand the common messages. The seventh-dimensional seed planet as a
celestial medium is a bit different. Celestial mediums can exist on
every planet, wherever there's a celestial mind. A lot of celestial
mediums will spawn before a planet's demise, right before the light goes
out. This has happened on other worlds. To save their own life force,
the celestial mediums travel into the future, to an endpoint of its
consciousness, just before the light of the planet --- the literal
stream of energy --- fades out completely. They locate the front point
of their earliest celestial mind and absorb it, then they seed their
celestial mind on another planet.

The life of celestial minds is inspiring, like everything else in
creation. It's really just one thing happening at different levels. Just
as the white wisp of seedling leaves the dandelion with the slightest
wind at just the right time in its cycle, so too are the seeds of
celestial minds blown from one field to another, one world to another in
this scale. It's just life. No different than the turnings of nature
here. Celestial minds have their own astral worlds. They have their own
life reviews. They possess a variety of means to stave off death,
natural processes by which something is spawned from their world.

When we have elevated ourselves, we transfer consciousness of our
allness to become the celestial medium of peace. It operates in the
physical world, the red and blue road, and on the celestial road with
its many brothers and sisters. We learn through astrology how different
worlds affect us. We work with celestial minds which incarnate into our
world and other worlds, both physical and non-physical, and as entangled
and unentangled observers. We work with them at the celestial medium
level.

Becoming a celestial medium of peace is our birthright. The journey is
linear at first then it becomes fully non-linear. The linear process is
self-mastery. We come to understand the length of our waveform, how
strong and potent we are. This is so when we can go through the
conscious choice to become the celestial medium between celestial minds
and surface minds for the generation. We learn how to bring unique
concepts of peace to places and space of time that are looking for that
medium to inspire new layers of peace. As more people come into
celestial mediumship, the global narrative will become more irrelevant.
Humanity will slowly realize the global narrative is irrelevant to the
bigger streams of time. We will detoxify from roman numeral time, and we
could probably enter a system of commerce beyond the Babylonian money
system. There are celestial exchange systems that allow matter to matter
manifestations from one density to another.

The celestial medium of peace role is not for everybody. It will be a
percentage of the population. The celestial medium of peace souls had
the contract to do this twenty or forty years ahead of time. It has been
seeded in the three to five previous generations. The event is being
prepared. The celestial medium of peace group is a kind of celestial
support system. They are creating concepts and language to navigate the
changes. The celestial medium of peace will be there for anyone to
connect with our planet.

\subsection{Crystallization}\label{crystallization}

During the awakening, it's vital that our DNA crystallizes. It's so new
strands of awareness have the fluidity to grow, like a plant, and create
solid neural pathways into many different dimensions. In a sense, we are
the future us. and there will be another future us who is a lot closer
to the \emph{awakening}, and our stream of light lengthens from an alpha
to a theta pattern. When our wavelength lengthens, the experience
becomes more dense and rich. Full fluidity means no internal limitations
of spirit stopping you from creating incredibly potent memories backed
by faith and spirit. By manifesting the dream as a tangible feeling,
people can taste, touch, know, sense, smell, feel, and experience. Many
people taste hearing, or hear through taste, or both. When it becomes a
tangible experience, it has many unseen languages behind it, defining it
more by making the dream-space tangible here and now. It's that journey.
Make everything real now. Open up the akashic records, here and now, in
this moment. Then it can be crystallized into our greater form of
growth. It's not just observation. Sometimes the lineage has the
awareness built into it, and people go through awakening based off time
locked experiences.

\subsection{DNA}\label{dna}

DNA is part of the founder's technology. It is the connective tissue
from the ocean of awareness and sea of consciousness to a light based
wisdom, intelligence, and consciousness for any animated biological or
non-biological entity. It was fundamental when this universe was being
created, a unique experience compared to other universes. There are many
variations of DNA. Non-biological DNA is solidified matter which can
have DNA based rungs and structures within its growth patterns, with its
own inherent intelligence. The crystal and mineral communities don't
need to walk to have an experience. Walking is a unique experience. An
entire line of creation springs from it.

The DNA strand organization, or the strands themselves, create the weave
of the DNA, the encoding of the strands. Every strand represents a
different level and capacity of memory storage. They enfold into an
implicate order of greater awareness. DNA can store frequencies of time.
This how we remember past lives, but not the only way. There are other
ways to remember past lives. The organization of your strands, and the
rungs that connect your strands, determine how much you can remember
from past lives. Certain strands block out all past lives --- negative
strands of wisdom and awareness. Many people within the awakening will
replace negative with positive strands. On the other side of the
awakening new strands will be added to our capacity.

DNA is eighty percent memories. This is a fundamental understanding.
Science and spirituality must realize this. We live in a photonic light
reality with rules --- how we incarnate, express, exchange, and pass on.

\begin{verbatim}
All the world’s a stage,
And all the men and women merely players;
They have their exits and their entrances;

Shakespeare  As You Like It
\end{verbatim}

DNA is the encoding, the soul. The light body is the cipher that decodes
and unpacks the experience. As we come back many times to the same type
of living, we store memories in DNA lineages --- bloodlines --- This is
how we imagine immortality in the infancy of self-awareness --- born
again and again into a lineage with our stored memories. Our soul family
incarnation process aligns us to the bigger concept of perpetuity. The
search is always for the immortal soul, the final state of being.

\begin{verbatim}
One generation passeth away, and another generation cometh: but the earth abideth for ever.

Ecclesiastes 1:4
\end{verbatim}

We don't teach DNA lineage on the planet anymore. We are looking at DNA
through the lens of the fourth industrial revolution. How can we hack
it, spike it, tweak it. We're like the monkeys beside the black obelisk
in Stanley Kubrick's \emph{2001: A Space Odyssey}. DNA is light in
another form, visible in one spectrum and invisible in another. Memory
is not physical. It's a form of light stored in an experience. ​​​​​​​As
streams of consciousness we have thousands of sub-carrier codes of
millions experiences inside us. We only need tune into the memory and we
can go into that stream of experience at any scale we desire.

Our forms are programmed to harmony --- the other twenty percent of our
DNA is not necessarily entangled with consciousness. Seven percent is
made up of harmony, frequency, and vibration. The remaining thirteen
percent corresponds to how the spiritual codes and contracts unfold in
linear and none-linear time, what agencies you work or don't work with,
and how no-time beings can consciously entangle with the time based you
to create a brand new contract that is need for change, auditing of the
self.

\subsection{Fairies}\label{fairies}

There exists entire realities sightly out of phase with humanity. One of
these is the fairy kingdom --- dwarfs and gnomes. We can't see them with
our eyes, but they are still here, layered into the reality. The sun is
what creates the fundamentals of time, the passing of the seasons, the
movement of the stars. Roman numeral time has tried to hijack our
awareness of that to make it central focus of our mind's resolution of
time. Places of power, which naturally attract us, have thinned veils
between the layers of reality. Our consciousness has more capacity to
perceive, receive, understand, and interact with the usually unseen
layers of reality. We are more in the quantum field than the chemical
frequency in these locals. A closed person visiting Normandy won't see
the other layers of reality. It's just a memorial, but the veil in those
places is very thin, nevertheless, the chemical reaction stops closed
people from seeing the other side. Tapping into the deeper layers of
reality is based on how tuned in you are to allow those experiences. The
\emph{I am} as the experiencer, fully in the vagus nerve, is
intraconnected and interconnected, and can simply experience different
levels. The \emph{I am} as the observer can observe but not process the
data.

\subsection{The Farm}\label{the-farm}

There are many boogeyman stories out there. Every culture has them. It's
the devil in Christianity, Satan is Islam, the archons for the Gnostics,
the many and varied monsters of HP Lovecraft, and too many more to list.
They are all fundamentally true, or, a better way of saying it, is that
they are contextually true. There are two gradients of truth that must
line up in any investigation --- details and context. If you get the
details right in the wrong context the truth will not unlock for you,
and if you get the right context and the wrong details you are similarly
locked out of the truth. The context of our situation has always been
correct. We are beset by negative, regressive, parasitic creatures which
impede us, slow us, and, in the worst cases, control and dominate us.
The truth is the earth is a genetics farm. The only real commodity in
creation is genetics.

Our infinite source energy is the harvest. The DNA farming technology
allowed them to tap into the fundamental source of the exchange system.
It's manipulating the galactic commerce and exchange system. The global
narrative, the disinformation stream from the control system on the
planet now, simulates the galactic commerce market, but, in doing so, it
mutes it to a planetary narrative. That is an imposed limitation. Our
connectivity goes into all the dimensions and right back to the source
of time and life itself. They created false gods. We were entrained to
worship them. These false gods were the first idols of awareness. They
were deliberately created to minimize our experience of reality by
minimizing what we imagined to be reality. He who controls context
controls the debate, the oldest maxim of debate, retaught to successive
generations right to this day at Oxford, Yale, and Harvard. The first
gods and religions limited our consciousness growth and entrained us to
hierarchical order --- \emph{right away governor, his lordship's
permission to speak}, and a million other linguistic artifacts of mental
colonization. Our spiritual birthright and legacy are robbed. When
someone popped into remind us --- and her you can pencil in a near
endless list of sages, shamans, prophets, mystics, and masters --- they
were dealt with swiftly and harshly, especially if the message spread
too quickly. We are told it's difficult to learn how to walk --- baby
steps! --- and never even told we can fly. Where people lived through
the lies, usually in native cultures, they correctly adduced their
environment was a living lesson of what human consciousness can do.
Nature has an eagle, so, naturally, a human being seeing the eagle would
try to imagine what the eagle might see from that vantage, then, lo and
behold, they realized they could fly without wings, that their
imaginations were doorways to higher consciousness, and it was good and
right until the Jesuits mercilessly massacred them precisely because
they were spiritually toxic and infectious, corrosive to the created
gods narrative of the \emph{civilized} peoples of the world.

To disentangle from the global narrative, we have to temporarily accept
the third dimension as our infinite source-connected space, until we
realize the fourth dimension is a bridge dimension to new strands of
dimensional awareness. The surface world becoming more dense with light.
Our Solar System is moving into into the eighth color of time, a
\emph{galactic groove} with more light. Acceptance of the third
dimension means going back to natural living, back to simplicity, being
present in the body, using this time now to heal, to nurture and nourish
the incarnate life form. Inviting joy, bliss, and pleasure back into our
lives, fulfilling part of the original purpose of coming here to earth
--- the grand enjoyment and creation of life, the journey from finite to
infinite, death a simple marker point for the translation before
entering the infinite frequency again. In order to fully engage in this
experience, to spirituality understand, we have to take the mystical out
of mysticism to engage mystical and magical synchronicities. Part of it
is the great forgetting at birth.

\subsection{Fertility and
Spirituality}\label{fertility-and-spirituality}

There's an eye in the heart often activated through child birth. Women
can see through this eye in the same manner we see through the third eye
in the forehead, the imagination center. The menstrual cycle is a way
for the rods and cones to align with the third eye plus the ones in the
heart, rectum, or clitoris, all extensions of the third eye. A man's
third eye can travel to the tip of the penis and connect into the womb
portal from there. Menstrual cramps and pains are often a sign of being
out of alignment in those areas. A most beneficial prayer technique for
women during their cycle is to call in all their thoughts, ideas,
constructs, and energies from previous menstruation cycles and detach
from them on a month to month basis. These powerful times for women are
being high jacked and bastardized by the global narrative. The menstrual
blood is very powerful as an energy of being a negotiator, an
arbitrator, or peacemaker.

Menstruation continues after menopause. Women still go through the cycle
without blood. The fertility spirits attached to menopause move on to a
higher density. The DNA is no longer producing the unique experience of
bleeding, but the spiritual mechanics remain the same, even more
intensified through menopause. In most cases when women experience heavy
menopausal symptoms, they're actually giving birth in other simultaneous
realities which need the births. Their remaining fertile life alters
versions of themselves who didn't get pregnant. Using their biological
clock, they find a signature frequency match to complete
interdimensional birthing as part of their karmic resolution.

Hot flashes can happen when an alternate version of the woman is
breaking water and is more than likely going to die from the birth. they
are transferring chemical life force based on their experience to avoid
this. A hot flash can also be another version of you, in another place
and time, and in an alien form, in which the birth got difficult.
Birthing is part of karmic resolution. This is important to remember.
Through strands of awareness in the DNA, the connective tissues transfer
life force to assist in that birth by another simultaneous version of
yourself who lacks fertility power or lives in an environment with no
fertility at all. This allows the mystical births to happen, the babies
who should never have survived or lived. Evening primrose oil is one of
the natural remedies for hot flashes. This plant oil is harvested as an
essence to lessen the effect in this reality and, at the same time, it
amplifies the experience on the unseen side.

Some strands in the DNA need a special chemical soup in the body to
activate fertility. It used to be manipulated in the overall chemistry
of the body. Other strands had more opportunities to awaken. When a
woman who never gave birth is going through a very difficult time during
menopause, another version of her simultaneous existence is going
through a birthing experience. They are both be intrinsically linked to
reduce the negative effect. There are times when co-living souls go
through menopause together, This generates new life in celestial
nurseries. It gives birth to a new soul frequency in the ocean of
awareness. The new soul frequency begins the journey into the sea of
consciousness and manifests in time and space.

The fatty deposits around the midline during menopause serve as a
protective membrane, but it can block good experiences with regards to
working with a woman's residual image. Once the biological fertility
clock stops ticking, the \emph{awareness clock} takes over. We can gain
a greater awareness and perspective of the awakening. We can experience
mood swings when the body is trying to find the right chemistry. It's a
balance between overproducing and underproducing hormones and chemicals.

Men go through menopause too, and they also have their individual
process through cycles of creation. As they actualize their physical
manifestations, a house, artwork, business, what have you, they leave
their legacy for their clan, tribe, nation. Men build an archive of
experience that stays manifested in time and space. Lineages in the
unseen can plan lives through the infrastructure created by the urge of
manifestation. Men reach their sexual peak around the age of eighteen.
Women reach their peak in their thirties. This is why it's important for
the infrastructure in the unseen to be planned. The cycles have been
manipulated by DNA farming. If the human reproductive cycle was not
manipulated, most pregnancies would be eighteen to twenty-four months.
In some instances it can be up to five years. In the past, the umbilical
cord wouldn't be cut for months. This allowed more bonding between the
partners. There was more opportunity for the father to have ritual
connection to the child through the mother as the medium of the
connection.

Testosterone drives creativity in men. There are other things similar to
testosterone that drive construction. A male scientist doesn't use
testosterone, but he uses another version of it, a mental aspect of the
testosterone. There's no scientific name for it yet in this reality.
There are several hundred forms of testosterone, each with a different
chemical chain that allows a different aspect of creation. Through
manipulation of our bodies we are not producing the all encompassing
testosterone which keeps us in fight, flight, or freeze. Our glands have
been manipulated to produce one strand of testosterone over the other
which leads us back to the cerebellum in the motor cortex.

The birth control pill is manufactured from giant farms of female
horses. The urine of a pregnant horse is the chemical basis of the birth
control pill. The horses are pregnant their entire life. Their colts are
taken and chopped up into horse meat sold to pet food manufacturers and
fast food restaurants. The entire industry revolves around the urine of
pregnant horses for human birth control pills. Many women reject the
different types of pills. There's a malaise associated with the pill
they can feel. They become worse and worse until they get the birth
control pill out of their lives. Before the horse urine birth control
pill there were plenty of natural herbal remedies to stop pregnancy.
Like most lineage medicine --- ayurveda, traditional Chinese medicine,
homeopathy, naturopathy, and others --- it was delegitimized and
marginalized by the big allopathic medical footprint that coincided with
the big push into the twentieth century economy, in which everything was
patented, synthetically replicated, restricted to \emph{licensed}
practitioners, taxed and brought into the mercantile system.

\subsection{Karma}\label{karma}

It's very easy to create karma through unawareness. It's really the
purpose of karma. Karma is unawareness. The karmic cycle produces
awareness. Karma is the simplest of things to understand once you build
into the divine hologram. It begins in our vaguest of awareness, a
silent petition, a nudge for experience, then, somewhere in time we meet
the circumstance that matches the silent petition. We sign the contract
and we cycle through the karma. We live the experience, first as an
inner realization of what the impulse was, then the manifestation, then
the realization and participation of others drawn to the karmic
circumstance you have created, as you will be drawn to others in an
effort to resolve your karma, and then the co-creator edits our creation
in the form of, you guessed it, karma.

All of it is tied together by this sound and light that animates all the
worlds where we create. I suppose a canvas would be an appropriate
metaphor. We are an aspect of that which generates the sound and light.
We are an aspect of the prime creator. We can co-create in the divine
hologram. It's all a co-creation down here, at least insofar as human
beings are concerned. But we own what we create through cycles and
consequences we didn't anticipate when we created. This is the law. Own
what you think, feel, and do. Of course the law is oft abused and
circumvented. Karma dumping and swapping --- read scapegoating here ---
is an active market for third party consultants: ritualists, black
magicians, wizards, artificial intelligences, influential entities, and
too many more to list here.

Let's take a simple, commonly experienced karmic pattern in our
post-modern human life --- the dysfunctional relationship. Remember the
last time you were in one. Now remember when you allowed yourself to
contemplate leaving the relationship. You felt elated, right? It was a
mixture of fear, elation, and tension. Your precognitive workforce
foreshadowed your emotional state. That's how you were able to feel it.
You borrowed emotions from an as-of-then unlived future.

It's possible to have a parallel set of experiences. There can be two
parallel and simultaneous expressions of you existing at decision
points. The simultaneously existing \emph{I am} chooses to walk out, but
you don't, or vice versa. It makes no difference. There's an infinite
number of reasons why parallel cross overs happen. It balances out the
old karmic journey and creates a new one --- the law of entanglement.

The great awakening transcends karma. The awakening is the end of karma
as universal law. Karmic entanglement is no longer to be used as
universal law. Consciousness has evolved in our part of the galaxy. The
simplicity of karma can easily be intentionally abused. It can lock
beings into servitude without end. The great awakening is going to
backstop it. A new system of resolution for thought, word, and deed is
coming into place.

Karma as an entanglement experiment describes a quantum state that is
not entirely independent of other states, whether or not the individual
objects are spatially separated. As a result, measurements performed on
one system seem to instantaneously influence the other system(s)
entangled with it. None of the entangled states are isolated from one
another. Let's look at Einstein's spooky law through the disentanglement
and entanglement of the incarnate life form to source. There's the
entanglement within the hologram of a planet surface --- subsurface and
astral timelines --- Separate from its surface timeline, which is a DNA
farm cultivated for harvest. In this instance, which is the example of
earth, source connection and disconnection become a primarily surface
based experience. That experience as a choice based process promotes the
unlimited point of view --- entangled and unentangled observer and
experiencer of the universal and galactic sources --- even though we are
still embodied on a planetary surface separate from the solar system's
awareness. Earth is a unique place of mass DNA farming. It can lead to
mass awakening through individual choice and responsibility.

The person creating an experiment is creating a construct that has
connective tissue in the unseen world. It allows data transference from
the unseen layers of one DNA frequency to another. Certain people have
windows in the unseen layers which allow information to bleed through.
It bleeds through the five senses --- as a processing system --- to
create a limited form of awareness in the entangled connected tissues.
The five senses create the sixth sense, the intuition and awareness of
it. These connective tissues are all in the DNA.

Our DNA is entangled through the fetus in the womb planning. It sets a
multitude of potentials omnidirectionally. There are plenty of people
within a family who don't have a great connection to each other. It's
purpose is revealed in the spiritual contract. Look at entanglement
through thought constructs. An example is living with a person for a
long time and generating a point of view about them. The construct makes
for very easy interaction because of the many neural pathways between
the two people. This creates additional pattern recognition, which
results in more thoughts. We then project the entire thought construct
onto that person. The construct must be broken at some point because it
will impede objectivity. It will become the norm. We create and break
these thought constructs, the conscious aspect of entanglement.

We are not stuck in reincarnation. We incarnate and reincarnate. In the
first part of our lives we might be a reincarnating soul. If we break
through the false propaganda we may become an incarnating soul. Or we
start as an incarnating soul, then run into a karma cluster that makes
us into a reincarnating soul, repeating karmic cycles --- a rinse and
repeat that doesn't stop until you break out of the karma. You can be
both at the same time. It depends on your ancestral lineage.

\subsection{The Literal Metaphor}\label{the-literal-metaphor}

Observation is also implicate order awareness. The observer effect
should not have come so early in the crystallization process. Some
people can have a three sense observation and still access the ocean of
awareness --- another bloodline influence example. Free will is tainted
by the bloodline. We grow additional strands of awareness. The ocean of
awareness and the sea of consciousness crystallizes and changes the
bloodline at a certain level of acceptance and integration. This is the
journey of the celestial medium --- \emph{I transfer the allness of
myself to become the celestial medium. I no longer need to grow in this
narrative. The next narrative I grow is in the spiritual commerce
network.}

We are hypothetical beings. We can believe in many things. The universe
determines what manifests through our wills. Hypothetical becomes
\emph{I am}. It's realized through engaging our belief engines which
allow strands of awareness to influence intuition --- precognition and
postcognition --- without competition or hierarchy. A multidimensional
being manifests into this third dimension through created tangible
experiences co-created with the infinite celestial medium. The incarnate
life form is the expression of the present, the here, the now.

Epigenetic urges influenced by past memories often keep us from creating
new experiences. We have lived billions of incarnations. It's vital we
disconnect from them and reconnect with source. This is the way to
create new memories, which is part of the awakening journey. We
sometimes over-identify with aspects of our evolution. Identity as myth
is rarely explored, but it can hugely influence the way we experience
life, and how we create in it. The more we identify with one part of our
journey --- grand earthly masters of manifestation or spiritual
celestial mediums --- the more we limit ourselves and inhibit our access
to the possibilities of the many divine holograms. Buckminster Fuller
immortalized the phrase --- \emph{I seem to be a verb} --- when it came
to considering identity.

\begin{verbatim}
I live on Earth at present,
and I don’t know what I am.
I know that I am not a category.
I am not a thing — a noun.
I seem to be a verb,
an evolutionary process — an integral function of the universe.
\end{verbatim}

Identity is a strange thing. Thought is not static, It's a process of
movement. Different metaphors in our belief engines change the very
nature of the internal representation. By looking at celestial
mediumship from this different perspective, we can change the way we
identify with it, gain clarity and ease on how we interact and work with
it. Ask --- \emph{what does celestial mediumship look like for me} --- a
ship that helps us sail through the ocean of awareness and the sea of
consciousness, a vehicle we sit behind, a building we construct? It's
all about the unique way we internalize the subject matter to fractalize
the strands of information, enter it to cognition, and realize it in the
here and now. Talk in pictures. Metaphor may be alchemically
internalized as an expression of a multidimensional, multifunctional
being of photonic light.

\subsection{Mandela Effect}\label{mandela-effect}

The Mandela effect is the karma of all those who've been manipulated
throughout time, as well as a bleed though from other times. The system
has shifted our reality and moved soul shards on to other realities so
our memories would be fragmented. It is a way for the universe to put
everything back to neutral and help us to find the forgotten pieces of
ourselves, the pieces and parts that has been manipulated and put
outside of time.

In the \emph{Mandela revocation} we get all the fractured pieces ---
lost and found implicate orders --- together for the celestial medium of
peace journey. There are versions of ourselves lost in void space who
never got resolution and we, as the manifesting being of the now, can
resolve that paradox through creating experiences and legacies. Through
different perception and perspective we can generate manifestations on
the forgotten side so they are no longer forgotten and the system must
now deal with them as remembered not forgotten.

Forgotten selves are selves who no longer have a frequency of time in
the celestial karmic system. As we enter the celestial medium journey,
we can reconnect to the spiritual celestial commerce exchange market.
Originally here on earth, there have been certain beings and
technologies such as the different galactics, the DNA farmers: Elohims,
Reptilians, Orions, Annunaki, Arcturians, Sirians, who had different
ways of perceiving the galactic commerce network through technology.
They began manipulating the flow of energy between star systems with
technology even though they had not achieved celestial medium status in
their spiritual journeys. They were entangled observers using technology
that had simulated unentangled observer technology. This allowed them
manipulation within thousands of years instead of millions of years.
Those original DNA manipulating beings thought they were Gods. They kept
manipulating DNA and the flow of energy between celestial sources
allowing them to farm all DNA on a grand scale.

The forgotten selves are part of your forgotten workforce. They are
trying to get back into the zone where your precognitive workforce can
perceive them. They are aspects no longer connected to the nonlinear
soul. Their original linear time was erased. They are trying to get out
of this erased time back into non-linear time. There is a network of
forgotten selves that works together to be remembered. The Mandela
effect is a broadcast to all forgotten selves in awareness, unawareness,
time and no-time. Wherever life has gone, even if it has been erased,
there is an opportunity, a portal back to the hub of interconnectivity.
It can be perceived as the trans-galactic exchange system between eras
of light. Those forgotten selves will integrate with your precognitive
and postcognitive workforce and no longer be forgotten but remembered
and added to our akashic record. They have not been part of your AR
being in forgotten space.

.. AR being??

They can represent themselves in infinite amounts of ways. It all
depends on how long they have been forgotten and what gifts they have to
offer. At the end of the Mandela revocation you are talking to every
forgotten version of yourself, so everyone of your peacekeepers may be
remembered and reconnected to the fifth world of peace, the unvanquished
dream in all existing realms. The original founder beings moved on to
other universes. Our other selves are the ones searching for the lost
Mandela effects. It is our responsibility to indicate to our
precognitive and postcognitive workforce that it should be a priority to
find every aspect of our forgotten selves up to nine hundred degrees of
separation from us in this phase of awakening.

\subsection{Mind Heart Gut Super
Highway}\label{mind-heart-gut-super-highway}

Sometimes the mind processes better than the heart, or the gut, or the
other way round. Then there are certain pieces of information where the
mind, the heart, and the gut have to work together. Once the
mind-heart-gut starts working together, the analogical side of the mind
--- which compares two things --- gets stronger, along with the
empowered programs that are with it. This is why daily practice is so
important. Locality and non-locality are still based off the brain's
time-space location, which is a marker signifying an anima of awareness
and a flow of data. We use the brain to interpret inter-dimensional
frequencies of the multiple versions of self. The brain is the
instrument of experience. It has a gut-brain and a heart-brain, each
with its own observance/ This allows processing of different time or
no-time. Brain, mind, heart, and gut space are different natures of
experience combined into one experience.

DNA communicates within the physical form. It communicates from form to
form through incarnations. It communicates between incarnations. It
communicates to our light bodies. It has the ability to go from chemical
to light. This understanding allows reasoned contemplation on many
consequence theologies, the wages of sin, the sins of the father, and
karma itself, whether applied to an individual, a family, a community, a
geography, or any other distribution point; it's all one DNA
communication network, the prime creator's backbone for several layers
of experience, straddling light and chemical, which correlates to the
physical body and the light body. We are simultaneously living \emph{I
am} versions of ourselves, scattered through time. In low consciousness
these other selves are unrecognized. To quote Roy Batty from \emph{Blade
Runner}: like \emph{tears in the rain}. In higher consciousness, our
awareness permits communication to multiple selves, the consciousness of
the earth itself, and beyond.

The \emph{I am}, as the incarnate life form, occupies and entangles
consciousness within the body through three stages. One, the
consciousness is in the brain-heart-gut. The brain-heart-gut complex
links to the central nervous system. The central nervous system connects
the entire fascia system through the vagus nerve --- the central nervous
system connector --- as part of the DNA communication system. Two,
consciousness is in the sympathetic nervous system (SN) and the
parasympathetic nervous system (PSN). Three, consciousness is in the
entire neural pathway network, fascia, dermis, hairs, the entire system.
It connects to the gallbladder which is intraconnected to the vagus
nerve. Every organ is intraconnected and interconnected to the vagus
nerve.

The life form is part of the individual and collective experience. Our
life forms are on all different levels of awareness --- planetary,
solar, galactic, and universal. Contemplate the vagus nerve aligned to
our magnetic North and South Pole. The sympathetic and parasympathetic
is our local space time. The sympathetic drives our daily actions when
the soul is in the body. The parasympathetic drives the body in lucid
dreaming and other spiritual states, or when it is fully in
self-defeating programs. The sympathetic can also be self-defeating and
kick the spirit out of the body. It's driven to resolves karma. It
guides us like a compass to choose a variety of karma out of free will.
The vagus nerve is connecting to the North Pole, our ancestors, and to
the South Pole, our future generations. We need to reclaim the vagus
nerve as the truest spiritual sovereign authority we have.
Parasympathetic and sympathetic programs can kick us out of the body. A
sympathetic example would be road rage, rebellious energy for the most
part. When the parasympathetic takes over and thinks it is the soul the
ego and the shadow have made an alliance inside each other to manifest
an internal villain, a bully, so the soul can't be in the body. In
Jung's psychology the subconscious looks upon the sympathetic as fight,
flight, or freeze, and it looks upon the parasympathetic as rest,
digest, and relax.

Entanglement is the measure of how much consciousness is in control of
the body. It is measured through the vagus nerve, the sympathetic
nervous system, and the parasympathetic nervous system.

The subconscious rest, digest, and relax vagus nerve connection is when
we are in those spiritual moments where we are reclaiming our authority,
taking back our power and purging the vagus nerve. Once we fully occupy
the central vagus nerve with our consciousness, we can flow it directly
into the sympathetic and parasympathetic nervous system. This is how the
incarnate life form can retain lucid dream creations. This explains why
people run by programs have difficulty lucid dreaming. It's difficult to
make rich, high quality memories. The vagus nerve and the
parasympathetic are connected to mystical experiences. The sympathetic
has neural pathways designed to use the five senses. The five senses sum
to the sixth sense, the totality of the experience.

Think of a violin. The parasympathetic system is the body of the violin.
The sympathetic system is analogous to the strings on the violin. The
vagus nerve is the bow. Consciousness plays the violin. The
consciousness of the earth itself is the conductor. The parasympathetic
system is the resonance chamber. These things are useless alone. The
string is nothing without the bow. The vibration is nothing without the
hollow chamber resonating with the body of the violin. The fine tuning
relates to how much the soul is in the body.

The consciousness of the planet is the conductor. It hands out the sheet
music, the larger composition to which the individual instruments
contribute --- the blueprint of synchronicities. Returning to our linear
ocean of awareness metaphor, the planet is the interconnection so the
body --- the life form --- can have an intra experience with the planet.
This may be alone, with individual family members, cultures, religions,
anything in the sheet music provided by the consciousness of the planet.
In this orchestration we seek harmony to make direct signature frequency
matches. The planet simultaneously exists in the ocean of awareness and
the sea of consciousness. The planet's celestial mind is the medium
between these two levels of awareness as well as the planet itself
manifested in time and space so that beings living inside it can have a
s set of unique experiences. This applies to every planet in the
universe, with only a few exceptions. The celestial mind of the planet
is intraconnected with the celestial mind of us, the life forms, as well
as intra connected with the ocean of awareness and the sea of
consciousness manifesting in physical and non-physical space.

We want vagus nerve, sympathetic, and parasympathetic sovereignty. This
permits intra and interconnection to our celestial minds. The journey is
in maintaining sovereign connection as an ongoing experience until the
experience is second nature. At this unfoldment we can achieve other
forms of embodiment. We can leave the body and not lose control of the
three aspects of consciousness entanglement. We can create versions of
ourselves in other places, spaces, and times. This is our legacy as
multidimensional and multi-functional beings. We can adapt form to
communicate with other places, spaces, and species. Sovereignty is
earned when the soul can leave at will. DNA was designed so when we
reach a certain frequency we are no longer solely within chemical
experience. Chemical exchanges are fundamental to the life forms living
in this third density. Our journey is from chemical to light. The water
--- the fluids --- that comprise the atoms of our bodies become a
resonant amplifier. Light based experiences happen through the
refraction of water. The soul is the light inside the body. The water
and fluid are refracting it by chemical reaction. When you shine light
through water or a prism there is no chemical separation of the prism of
light. Thoughts can be implicate and explicate at the same time ---
orgasmic experiences, love, and fundamental experience without thought.

Reincarnation was a trap that created karmic entanglements. To get back
to celestial mediumship, reincarnations are optional and free willed for
karmic resolution. We achieve multidimensional living and realize
leaving here was never truly the goal. Multidimensional existence is the
goal. We can generate a part of ourselves that continues the journey
while having many other parts of ourselves in other places. The \emph{I
am} apex presence roots uncontested in the here and now. Reincarnation
and some forms of incarnation became competitive reduction journeys. The
entire experience of death is set to change. Our lives will go to three
hundred years, five hundred, seven hundred years in one go. The passing
over experience will persist to finish this era of light's karmic
accounts. Our capacity to plan future lives with twenty to thirty
percent of our life memories, hundreds of millions of years as our
database for mapping future lives.

We're not put on our mother's heart for days after birth with the
umbilical cord connected. This is the natural law of harmony. It's so
simple the slightest sophistry devolves us of spiritual inheritance.
Birthing in hospitals with \emph{licensed} medical personnel and limited
bed time due to economies of utility does not complete the first
synchronizing of the child. Our \emph{I am} technology has to come out
quickly in our body in the present system. Everything is set to slow
down. The future will see more natural birthing. Pregnancy will be
between nine and twenty-five months.

There are children here now with a good part of their memory available
to them. They might be ahead of time and lack parental guidance. The
fetus in the womb planning is set to change as well. The mother and
father will co-plan the spirit journey before the fetus even enters the
womb. It will be light based planning from the outset while fully
incarnate in this third density. This is multidimensional living. This
is the great leap forward, no offense to Mao Zedong. He had the concept
right. It was the context he lacked. A whole new human race is ready to
step out of the chrysalis of time and spread its magnificent and
colorful wings. This is the promise.

\subsection{Mineral Consciousness}\label{mineral-consciousness}

Crystals and rocks are communities of beings that are part of the sea of
consciousness, too. Crystals are part of the implicate and explicate
order, simultaneously entangled and unentangled. We can imprint
entangled narrative perceptions and agendas upon crystals with our
precognitive workforce. A crystal will do what it needs to do for us
based off how our precognitive workforce manifests the matter. They are
part of the ocean of awareness that becomes part of the sea of
consciousness as animated matter. Crystal allows us access to the ocean
of awareness and the sea of consciousness based on our capacity to
perceive, receive, process, and manifest it. The crystalline structure
is materialized, no longer a fluid ocean of awareness or sea of
consciousness. When we enter the sixth and seventh dimensions,
crystallization is the lower end technology for generating matter based
awareness.

\subsection{Near Death}\label{near-death}

Near Death Experience (NDE) is part of spiritual contract to allow you
to see who, what, and where you've been in the life time since your
first breath. It might also be your past and future lives intersecting.
We often meet our guides, guardians, and others in the NDE. The body has
to go through the trauma of the death ritual. The aura somewhat pops and
the contained life force starts leaving the body. After the pop there's
a vacuum of energy. The body must produce more etheric --- chi, prani,
orgone, to name a few monikers it goes by --- energy and maintain it to
stay alive. The final breaths use the body's last alchemical fuel it's
had from birth. The brain loses the interconnectivity with the organs.
The organs remain a part of the divine hologram. The \emph{I am} begins
to disintegrate its structure. We go back to the ocean of awareness. We
may have attachments to who we have been in previous lifetimes. This
triggers life reviews and direct healing of the body. We connect back
into the original blue print of health. Some people have visions of
places and spaces of potential to refill the soul's capacity. Going
through this transcendence phase it's vital to maintain the auric bubble
around ourselves. If not we drain out our life force energy. We can come
back from a NDE an educated, illuminated being. Some people come back
with abilities they didn't have before, the ability to play the piano,
for example. It's a change in spiritual contract underwriting the
incarnation --- a new set of DNA based purposes. This is not a walk in
experience. Walk ins are extremely rare and often get misidentified with
NDEs.

NDE experiences take us out of time-space equations because we move into
the ocean of awareness then back to our life. Once we lose connection to
the organs it's just the vagus nerve and the spinal column reporting
data the body has gone through. We are disconnected from the hologram
because we are no longer supported by the aura. You can't maintain the
internal energy flow. It flows out of the body. Once we lose the bubble
around us we are no longer in the shared reality rules. We waver between
many different worlds including the ocean of awareness as our ancestral
connection. The sea of consciousness is more for the many dreamers
traveling back and forth, contracted with us on linear and non-linear
scales to ensure we stay invested in an era of light and don't check out
before our time.

As we leave time and space, depending on the kind of NDE we have, we can
go to a high density dimensional realm. This is when the fetus in the
womb had a grand goal not yet achieved. We can be sent to seventh or
eighth density to experience life from there then return with some of
those potent memories intact. Often people are so overwhelmed by the
experience. They are overwhelmed by their light being. It becomes an
expression of their self they fear they can't live up to. We can live
the light body. It's already who we are. The NDE shows us that. Those
experiences are contracted out in the fetus womb plan.

Bystanders sometimes accompany the soul when meeting loved ones on the
other side. Life reviews can be seen as random moments, even though
everything has an underlying universal order. When one has a life review
as part of their NDE it is about the spiritual contracts, help to grow
beyond them because the soul, in the internal and external
infrastructure, hasn't been able to resolve the issues. The fetus in the
womb plans all sets of experiences, including the NDE.

When doctors or nurses or family members perceive light leaving the body
that can be the etheric, the life force leaving the body at the end of
the transition process. This is actually a verifiable phenomenon. The
energy has light mass. The body is twenty to twenty-two grams lighter
after death. It all depends on how the life and death experience is
planned in the fetus. Some people have mystical deaths. These deaths are
another way of assisting others to mend broken faith. One such death was
the Catholic mystic and Trappist monk, Thomas Merton, who died in a
freak accident coming out of the shower, falling, reaching to a fan for
support, then electrocuting himself through faulty wiring in the fan. He
was attending an inter-faith conference in Thailand. The Buddhist monks
hosting the conference immediately defined it as a mystical death. The
terminology was not invented for Merton's passing. The mystical death is
one of four types of death in Buddhist teaching.

Out of Body Experience (OBE) is generally astral travel. This is
markedly different than an NDE. The astral body has an intact auric
bubble to store chi within the hologram. In a life review the \emph{I
am} perceives incidents from all different angles because of the
dissipated life force. The life force in the incarnation is the
foundation of the \emph{I am}. We may experience the pain we've
inflicted on others as if being in their bodies. It can be quite
dramatic. Many experiencers report an array of thoughts. Thoughts have
an electrochemical frequency employing the body's base electromagnetic
frequency as a storage system. This is how we create time stamps. In
near death experiences the body releases those energies. This is why the
thoughts come to our awareness. An infinite being in the ocean of
awareness can still experience these feelings as part of death. Physical
reactions help us acknowledge and resolve experiences once we return
from the NDE. As the body takes the last breaths a chemical reaction
persists for as many as seven days. This is attachment. The death
process can be dragged out in letting go of these attachments. In many
mourning rituals the bereaved stay with the dead body to honor and
witness the letting go of all the karma and dharma as an alchemical form
of resolution for the deceased and the bereaved.

The life review is part of the transition process and cannot be
bypassed. We all must do it. On the verge of death we don't necessarily
remember what to do. Some people understand death as part of the journey
and have prepared for it. Some people are in fear and panic over death.
Our guides and guardians assist us to begin the life review regardless.
Sometimes things we have deliberately avoided our whole lives come into
focus. An understanding of the preciousness of life is recognized in the
dwindling of consciousness. Death is a new beginning. It's a change of
energy and consciousness. Don't be afraid of it. Our choices in this
lifetime determine the ease we have with our life review. The
understanding of death expands consciousness and takes away fear. Death
is an acceptance to ensure that you have lived your life without
regrets.

We don't necessarily have all the higher levels of awareness available
when going through life review. When the life review starts the soul is
shattered into thousands of shards. The oversoul comes in and puts them
back together, takes out the negative soul shards and puts them into a
secondary file. Another fetus from another womb uses the soul shards to
integrate it into the infinite fetus blueprint choice so the shards can
get resolution in another lifetime. Soul shards are not the \emph{I am}.
The oversoul guides lifetime after lifetime.

\subsection{Personal Effort}\label{personal-effort}

We all have the birthright of celestial mediumship. Our ability to
inherit our birthright is conditional. We must focus on mastering
ourselves, healing ourselves, and nurturing ourselves toward our
inheritance. When I say inheritance I mean it literally --- the sins of
the father, the wheel of karma --- it's all inherited from our genetics,
but so is our greatness once we break the confines of family and
culture. Our true genetic inheritance is galactic and universal. This is
the greatest secret of the human race. This is why distraction is the
main tool of the enemy, anything to keep us from our true inheritance.

You have to be committed. All progress comes down to the ways we
integrate consciousness expansion with our daily life. The daily tasks
are good, observation of self and its relationship to the grander
design, contemplation of the mysteries, but it all must be done with the
goal of sovereignty to make it work inside you. It's what this is all
about, becoming the true self you are that knows itself in all
dimensions and realms. As the sages of various paths have said, you must
want it as you want breath. It must be vital to you. This is the chief
characteristic of the acolyte, the need to know, to prove to yourself
once and for all the soul is an immortal part of the prime creator, as a
drop of water is a part of the sea, and the sea flows out into the ocean
of awareness. We have access to the akashic records at our disposal.
This is the true reference library for all events, past and future.
There are no gatekeepers. There is no conspiracy. It's your birthright
as a human being.

As we are more and more in the state of celestial mediumship, we get
more information. It's the dividend of being able to stay at a certain
frequency for sustained periods of time. The expanded consciousness
blends into the moment. We become occupants of a multidimensional here
and now, with information coming in through the celestial mediumship,
while we are are fully in the here and now, walking around and
performing our daily routine.

We can't stay in high frequency all the time. We have to consciously
step down from those high states, otherwise we'd vibrate out of this
reality and all the work would be lost. Coming back into the body and
being present is vital. This is why so many internal paths developed
external exercises, like Chinese or Indian yoga to accompany the deep
meditation, the centering and grounding of consciousness through
physical exertion, concentration, respiration, and movement. This is
grounding of energy, no different than electrical grounding. How to be
present in all the innumerable worlds and times is achieved by realizing
we are not meant to stay in states of high frequency. We are not to
disrupt the blueprint in fetus plan. It makes it easier and simpler to
come back and enjoy this reality. Now changing states is as effortless
as breathing.

\subsection{Precognitive Sharing}\label{precognitive-sharing}

Our precognitive workforce is us. It is the understanding we can create
infinite conscious versions of ourselves and travel time, future and
past, and prepare a resource of knowledge and information we can
instantly call upon as manifestations of inspiration to beat anything
negative. Our \emph{I am} precognitive workforce is composed of
simultaneously existing versions of ourselves. These others have earned
the right for cross-time collaboration. There are negative frequencies
in this journey. We need to empower ourselves. The \emph{I am} in the
here and now declares itself a being of co-creation, absent competition
and hierarchy, a dreaming \emph{I am} breakaway DNA light body
civilization of one in this life form, the human being. We can use the
genuine work to make a great impact on loved ones, family, clan, nation,
tribe, and earth mother. If we choose to do this on all scales, we need
a masterful precognitive workforce, our birth right and legacy, to
create as a natural co-creative evolutionary being who is part of the
great dreamtime awakening. We use our responsibility to impact on the
loves of our lives, the themes and ideologies we promote to others, a
little dreamtime capital so they can find their own illumination, free
from gurus, without sending them down paths to false illumination. Our
precognitive workforce is there waiting to work with us, to think with
us, to love with us, to be part of our greater expression. We must put
the time, effort, and energy into understanding we can call upon our
inner geniuses from many dimensions, time streams, galaxies, and
universes to form a forceful collective, all of us, all part of this
dreamtime awakening, freeing ourselves from the limitation of the global
narrative.

Shamans have always used their precognitive workforce. Every generation
learns from the previous. We are a signature frequency match to our
precognitive workforce, and to the collective workforce of the highest
forms of our light soul teachers, all of the \emph{I am} instances as
part of our great hall of akashic records.

We tread on someone else's journey if we send out our precognitive
workforce to help them in a co-creational way. There's a fine line where
too much is too much. If the other being has no precognition, or any
form of understanding of what a precognitive workforce is, we are
stepping on their journey. Infants or young children who haven't formed
an \emph{I am} yet are okay. Most children don't fully form the \emph{I
am} until puberty, when the thymus gland creates three hundred new
chemicals that suddenly flood the body. This is puberty itself. It
solidifies the \emph{I am} technology as a time-space equation. When we
assist others with our precognitive workforce, we have an
interdimensional conversation with them whereby we join our precognitive
workforces to create a manifestation of synchronicities. It helps each
of the parties co-create an event which brings inspiration and healing.
Healers become facilitators. They amalgamate their precognitive
workforce with the precognitive workforce of the ill person. The ill
person may not have any consciousness skills. If those \emph{I am}
beings want to become true consciousness beings of choice they must
learn the process of self-illumination. There's an infinite amount of
teachers out there in the great dreamtime awakening. . Discover what's
the signature frequency match for you then go out, evolve, and create.

\subsection{Source Connection}\label{source-connection}

Source connection is living in the light worlds, the worlds above the
elemental and chemical, while grounded in the body, finite and infinite
at the same time. We disconnect to contrast being connected. It's an
aspect of the lesson here --- disconnection to understand connection. We
see this fundamental duality of the divine hologram everywhere --- the
yin and yan of the Tao, Carl Jung's extraordinary work on duality and
the shadow, the juxtaposition to the light. Not many voices have clearly
articulated the disconnection teaching before. The thread of life goes
everywhere in the universe, and that \emph{thread} has a connectivity
bandwidth exponentially beyond fiber optic, and yet we, this human race,
underwent the sensation of disconnection from source as an experience.
Realize what that means. We're like Chilean miners trapped in a
collapsed coal mine. That's how the connected species in the sentience
circus that is our galaxy see us, hardcore. As we have steadily moved
into self-awareness as a species, propelled as we were by Gutenberg, the
Western enlightenment, the Industrial Revolution, and, lest we forget,
the iPhone, we have seen this disconnection in the collective mind. It
rippled through with French Existentialism as chic twentieth century
philosophy, spurred on by the First World War, no doubt, the trauma of
it, the horror of it all. One of the earliest portrait's of this
dislocation would most certainly be Mister Kurtz, from Joseph Conrad's
\emph{Heart of Darkness}, the perfect literary tone struck for the
twentieth century, published in 1899, a harbinger if ever there was one.
We are here to experience disconnection from source. Oneness has no
meaning if we don't understand the disconnection journey first.

The disconnection fractal is achieved by controlling the mind. People
don't take a moment to realize the enormous changes the human race has
gone through since about 1890. We now live in a completely man-made
reality. We travel in an enclosed environment propelled by a tar plumbed
from the earth. We have face to face conversations a thousand miles
apart. We can drive past digital billboards in city thoroughfares. The
Greek amphitheater is Netflix, HBO, and the cable channels. Stonehenge
is Joel Olsen on a big sports screen, and the sacred is now profane.
This is spiritual conquest. This is disconnection from source. Literally
every artifact of our organic culture has been incorporated and sold
back to us. Yet, by reasons only explainable through cultural or
regional programming, we think it's unjust that Beijing select Catholic
Archbishops instead of the Vatican, and reincarnated Rinpoches instead
of the Tibetans. Regional and provincial narratives are more and more
folding into global ones. The global narrative teaches us false science,
false time by galactic timekeeping, false history, and belief systems
which long ago should have given way to tangible and productive wisdom
and knowledge traditions. False light is a multidimensional technology
commonly used here. This is the source disconnection.

\subsection{Spacial Awareness}\label{spacial-awareness}

Physical movement entangles us with individual and collective
consciousness, oscillating between explicate and implicate. We change
environment and move through different levels of consciousness. We alter
the existing. Our consciousness is acted upon by fluctuating fields of
electromagnetic energy. Epigenetics discovered our genes are made up of
fifty percent DNA and fifty percent protein. Genes are not
self-actualizing. The proteins comprise the structure of the human body,
defining shape and influencing behavior in an ongoing attempt to balance
charge and polarity from the environment.

Our individual bubble of reality gets enriched in experience and memory
through the journey on the celestial neural pathway. We go from one
hologram to another in the expansion we call the orchestra of
consciousness. The neural pathways are an assemblage of proteins that
move the body and help it to function. We all know how to walk through
this reality. The celestial mind generates the divine holograms through
which our bodies have experience. All living consciousness is part of
the symphony. The light and sound which creates and sustains all the
realities allows us to manage a fractal of it which we call our reality.
Our very reality on an individual by individual basis is a co-created
reality between us and the material of the hologram itself, sound and
light, which sustains our physical and inner existence. Our dreams are
expressed in sound and light. There are fractals within fractals.
Culture is another fractal, whether it be a pueblo in a mountain village
in Colombia, or the frenetic consumerism inspired by Madison Avenue.
It's a hologram overlaying and interacting with your personal hologram.
It binds us to an era of history. Our culture has Roman numeral time,
which is not our true accurate time stamp. It may use elements of it,
though. Our culture binds us to an era of history. It's part of the
hologram of resolution. Our entanglement into the culture's hologram of
roman numeral time builds up a weave into the individual hologram.

\subsection{Splitting Consciousness}\label{splitting-consciousness}

The soul can be split. We can be taken out of our original bodies and
put into \emph{simulated bodies} somewhere else. Consciousness can then
be broken into hundreds of different fractals. The fractals may then be
spread throughout time with individual missions. These are soul shards
of yourself, not \emph{I am} selves, bigger than normal shard pieces.
They remain connected to the \emph{I am} selves, but they are just
pieces of an \emph{I am} shattered into many pieces. The split the piece
itself still has access to the divine hologram, though the shards are
often convinced otherwise by the practitioners of this dark abuse.

\subsection{Superluminal Thinking}\label{superluminal-thinking}

Superluminal thinking leapfrogs chemical experience as the basis of
memory and consciousness. Let's look at it backwards through
photosynthesis. A plant eats light and excretes oxygen. Human beings
live in a chemical experience until light enters consciousness. It's the
reverse of plants. We consume elemental material here, calories, an
inherently chemical process, aided by a long digestive track, and we use
this energy, the fuel for the human experience, an integral part of our
chemical existence, to find the light in our consciousness. Creation in
a dual pole, free will space can often be navigated by bookends,
opposites, even irony as a conceptual understanding of the thesis,
because the opposites form contrasts, and, in a light based divine
hologram, without contrast we would not even discern the reality around
us. You see your reality, your wife or husband, your dog, you car
because the environment has light. The light finds pockets and
reflections, and it finds places it can't go, and from its presence are
all forms etched.

Superluminal operates beyond the zeros and ones of the sympathetic and
parasympathetic systems. The vagus nerve is fully functional. All the
chakras are open and interconnected through the central nervous system.
They are part of the superluminal experience. The body adds the
sensation that it can't process, but it knows it's the unentangled
observer in superluminal thought. The body grounds us here, but the
consciousness can go beyond the speed of light to tens of millions of
places and spaces simultaneously and collect millions of unique
experiences in one millionth of a second and come back with it fully
processed. Then we go out and do it again and again until our cup is
filled. Superluminal thinking is more than we have learned, read, and
studied. It's knowingness going to the next level, the next
apprehensible sphere of experience. It's subtle. We won't have conscious
cognition of it. Everyone has experienced it, Our level of practice will
determines how fast we can apprehend it. How is that possible? You're
already there. You just don't know it. You are unconscious to it. The
unconscious mind is connected to all knowledge. The conscious mind
creates a manageable data flow so you can persist in the illusion of the
third dimension. This is the basis of the Maya teachings in Buddhism.
Illusion was perhaps the wrong word. It's more like a projection of
light refracting through the atmosphere, the projection itself emanating
from the source of all our realities, the place without sound or light
that is neither dark nor silent, Kabir's riddle.

The sound and light is all sound and light, not just what can be
experienced within the human sense ranges for hearing and sight. All
these inner worlds and universes, if they are at all apprehendable, are
sustained by sound and light. Anywhere these two persistent emanations
of the prime creator are present we find contrasts and then forms and
then realities. It's this simple.

\subsection{Temporal Manipulation}\label{temporal-manipulation}

Our temporal awareness been manipulated. A lot of weaponized time travel
technology interferes with humanity's capacity to perceive time. We can
be heavily confused with our temporal awareness. Confusion is an aspect
of temporal distortion. It can be sped up or slowed down. Our temporal
awareness is unconscious to time speeding up or slowing down. Our
individual temporal awareness determines our perception and perspective
on how fast the algorithm can move. Separate from the vagus nerve, the
thymus generates temporal awareness between the brain, heart, and gut,
then all three separate from unity, making it easier to split
consciousness. In the connective systems between the thymus, brain,
heart, and gut is where you can highjack temporal awareness. That is
another limiting system that was put inside us, however, it has
backfired on the temporal manipulators. It gives us other \emph{backdoor
frequencies} of awareness through the temporal body.

Temporal highjacking has been around since the dawn of time. The whole
point of it is to manipulate our capacity to time stamp. Interlopers
discovered the infinite journey of soul then tried to figure out where,
when, and how they might create an incoherent pattern and get a soul
trapped in an era of history. They could then generate a global
narrative of mass distraction for the purpose of DNA Farming and hinder
the \emph{I am} consciousness from again entering the sea of
consciousness.

Temporal manipulation started forty-eight to fifty-five thousand years
ago. Not all life forms practiced temporal manipulation. It was about
limiting the amount of life forms on the surface of the earth.
Particular DNA lineages were not receptive to this temporal
manipulation. We went from nine-hundred thousand different forms to
one-hundred and thirty-five thousand. This is the basis of DNA farming.
This is how they manipulate and limit who is going to be on the farm.

\subsection{Thymus}\label{thymus}

The thymus generates the temporal experience in the body-mind-spirit as
a complex unit. It's called the high heart because it serves as the
doorway to our higher spirit to come into the DNA experience. In science
the thymus is called a one and done gland.

The thymus encapsulates the heart through the pericardium, which is
where it is originally created. When the heart starts to grow from its
original multi-cellular structure, it is the thymus that creates the
temporal awareness, and it remains there, assisting the magnetic flux of
the heart to harmonize with time. Inside the thymus are neural pathways
that allow the transformation, transmutation, and transfiguration of
multiple forms of time between the heart and the brain, the heart and
the gut and then the heart-brain-gut as a unified structure. The thymus
and the lymph system contain those special neural pathways separate of
the entire central nervous system and separate of the vagus nerve. It's
like its own Morse Code.

The Thymus is used, not the vagus nerve, because this is time itself,
gut-time versus heart-time versus brain-time versus unified
gut-brain-heart time. Imagine a multiple choice test --- fifty questions
in an hour, sixty-two seconds per question. This is the brain's
calculation of time. The heart measures the one hour as the potential of
the experience. The gut deploys intuition strategically into the
perfectly understood time span. This is the magic and mystery of
gut-time. It's been a part of our colloquial forever --- gut feeling.

A third of all our central nervous pathways are in our gut, a third in
our heart, and a third in our brain. It almost forms a kind of check and
balance system, not dissimilar to the executive, legislative, and
judicial triumvirate of power in the United States. When they work
together you have \emph{temporal awareness} --- three perspectives
unified.

The body-mind-spirit as a being has many forms of awareness. The brain,
heart, and gut are the triumvirate of temporal awareness. We receive
time and space and begin our map. Time creates space. Space requires
cartography. Cartography is the true mother of all art and science.
Without measurement we would not have been able to build. In one clear
aspect, all scriptures, both east and west, may be seen as inner
cartography, the landscape of the imagination.

A very unknown American poet, despite having won the Nobel Prize for
Poetry in 1955, Wallace Stevens, whose poetry itself was very much an
examination of the imagination as a human utility and as a universal
expression of nature and God, penned it beautifully in his poem,
\emph{Another Weeping Woman}.

\begin{verbatim}
Pour the unhappiness out
From your too bitter heart,
Which grieving will not sweeten.

Poison grows in this dark.
It is in the water of tears
Its black blooms rise.

The magnificent cause of being,
The imagination, the one reality
In this imagined world

Leaves you
With him for whom no phantasy moves,
And you are pierced by a death.
\end{verbatim}

The gut, heart, and brain possess deep awareness of the energies around
us. Electromagnetic frequencies are impacted by their environment. The
Schumann resonance is the unheard electromagnetic frequency effected by
solar winds. radiation, and planetary magnetics. This is how the
universal mind communicates to us and generates time in the temporal
awareness. It represents an opportunity for consciousness expansion.

\subsection{Unvanquished Dream}\label{unvanquished-dream}

The apparatus of infinite interconnectivity is the simultaneous existing
network of selves. This forms the hub of interconnectivity, part of our
precognitive and postcognitive workforce. The unvanquished dream is an
aspect of the infinite interconnectivity, giving us even greater
connection to all the versions of ourselves sharing that perspective.
The unvanquished dreamer of peace comes in here too. It connects to all
the forgotten and remembered oceans of awareness, the many seas of
consciousness, layered atop all form of thought, awareness, to connect
them in a single time-space location. It's a state of being that can
walk on time.

\subsection{Weather}\label{weather}

Weather is an intricate part of our history, part of what is going on at
the time. Weather is intraconnected to programmed water. The programmed
water of an era of history determines our weather patterns. We as human
beings are constantly imprinting on the water on an individual level to
create a collective. Animals and plants are conscious beings of choice,
even though they haven't been given the rights, duties, or
responsibilities of beings of awareness, allowing the experience love.
Our laws don't include them as part of that. The rest of the network of
life and our laws are separate from that through conscious entanglement
with the narrative. Trees, plants\ldots{}. anything that has
consciousness and experiences life as part of the planet. Our journey
into the great awakening is knowing the network that is out there. We
are responsible not to step on the journeys of all the other things
living here. As part of the great awakening the ducks, the dolphins, the
whales, all of them are part of the awakening too. It is not just solely
for us humans.
