\section*{Chapter 2}\label{chapter-2}

\subsection*{MIND HEART GUT SUPER
HIGHWAY}\label{mind-heart-gut-super-highway}

Sometimes the mind processes better than the heart, or the gut, or the
other way round. Then there are certain pieces of information where the
mind, the heart, and the gut have to work together. Once the
mind-heart-gut starts working together, the analogical side of the mind
--- which compares two things --- gets stronger, along with the
empowered programs that are with it. This is why daily practice is so
important. Locality and non-locality are still based off the brain's
time-space location, which is a marker signifying an anima of awareness
and a flow of data. We use the brain to interpret inter-dimensional
frequencies of the multiple versions of self. The brain is the
instrument of experience. It has a gut-brain and a heart-brain, each
with its own observance/ This allows processing of different time or
no-time. Brain, mind, heart, and gut space are different natures of
experience combined into one experience.

DNA communicates within the physical form. It communicates from form to
form through incarnations. It communicates between incarnations. It
communicates to our light bodies. It has the ability to go from chemical
to light. This understanding allows reasoned contemplation on many
consequence theologies, the wages of sin, the sins of the father, and
karma itself, whether applied to an individual, a family, a community, a
geography, or any other distribution point; it's all one DNA
communication network, the prime creator's backbone for several layers
of experience, straddling light and chemical, which correlates to the
physical body and the light body. We are simultaneously living \emph{I
am} versions of ourselves, scattered through time. In low consciousness
these other selves are unrecognized. To quote Roy Batty from \emph{Blade
Runner}: like \emph{tears in the rain}. In higher consciousness, our
awareness permits communication to multiple selves, the consciousness of
the earth itself, and beyond.

The \emph{I am}, as the incarnate life form, occupies and entangles
consciousness within the body through three stages. One, the
consciousness is in the brain-heart-gut. The brain-heart-gut complex
links to the central nervous system. The central nervous system connects
the entire fascia system through the vagus nerve --- the central nervous
system connector --- as part of the DNA communication system. Two,
consciousness is in the sympathetic nervous system (SN) and the
parasympathetic nervous system (PSN). Three, consciousness is in the
entire neural pathway network, fascia, dermis, hairs, the entire system.
It connects to the gallbladder which is intraconnected to the vagus
nerve. Every organ is intraconnected and interconnected to the vagus
nerve.

The life form is part of the individual and collective experience. Our
life forms are on all different levels of awareness --- planetary,
solar, galactic, and universal. Contemplate the vagus nerve aligned to
our magnetic North and South Pole. The sympathetic and parasympathetic
is our local space time. The sympathetic drives our daily actions when
the soul is in the body. The parasympathetic drives the body in lucid
dreaming and other spiritual states, or when it is fully in
self-defeating programs. The sympathetic can also be self-defeating and
kick the spirit out of the body. It's driven to resolves karma. It
guides us like a compass to choose a variety of karma out of free will.
The vagus nerve is connecting to the North Pole, our ancestors, and to
the South Pole, our future generations. We need to reclaim the vagus
nerve as the truest spiritual sovereign authority we have.
Parasympathetic and sympathetic programs can kick us out of the body. A
sympathetic example would be road rage, rebellious energy for the most
part. When the parasympathetic takes over and thinks it is the soul the
ego and the shadow have made an alliance inside each other to manifest
an internal villain, a bully, so the soul can't be in the body. In
Jung's psychology the subconscious looks upon the sympathetic as fight,
flight, or freeze, and it looks upon the parasympathetic as rest,
digest, and relax.

Entanglement is the measure of how much consciousness is in control of
the body. It is measured through the vagus nerve, the sympathetic
nervous system, and the parasympathetic nervous system.

The subconscious rest, digest, and relax vagus nerve connection is when
we are in those spiritual moments where we are reclaiming our authority,
taking back our power and purging the vagus nerve. Once we fully occupy
the central vagus nerve with our consciousness, we can flow it directly
into the sympathetic and parasympathetic nervous system. This is how the
incarnate life form can retain lucid dream creations. This explains why
people run by programs have difficulty lucid dreaming. It's difficult to
make rich, high quality memories. The vagus nerve and the
parasympathetic are connected to mystical experiences. The sympathetic
has neural pathways designed to use the five senses. The five senses sum
to the sixth sense, the totality of the experience.

Think of a violin. The parasympathetic system is the body of the violin.
The sympathetic system is analogous to the strings on the violin. The
vagus nerve is the bow. Consciousness plays the violin. The
consciousness of the earth itself is the conductor. The parasympathetic
system is the resonance chamber. These things are useless alone. The
string is nothing without the bow. The vibration is nothing without the
hollow chamber resonating with the body of the violin. The fine tuning
relates to how much the soul is in the body.

The consciousness of the planet is the conductor. It hands out the sheet
music, the larger composition to which the individual instruments
contribute --- the blueprint of synchronicities. Returning to our linear
ocean of awareness metaphor, the planet is the interconnection so the
body --- the life form --- can have an intra experience with the planet.
This may be alone, with individual family members, cultures, religions,
anything in the sheet music provided by the consciousness of the planet.
In this orchestration we seek harmony to make direct signature frequency
matches. The planet simultaneously exists in the ocean of awareness and
the sea of consciousness. The planet's celestial mind is the medium
between these two levels of awareness as well as the planet itself
manifested in time and space so that beings living inside it can have a
s set of unique experiences. This applies to every planet in the
universe, with only a few exceptions. The celestial mind of the planet
is intraconnected with the celestial mind of us, the life forms, as well
as intra connected with the ocean of awareness and the sea of
consciousness manifesting in physical and non-physical space.

We want vagus nerve, sympathetic, and parasympathetic sovereignty. This
permits intra and interconnection to our celestial minds. The journey is
in maintaining sovereign connection as an ongoing experience until the
experience is second nature. At this unfoldment we can achieve other
forms of embodiment. We can leave the body and not lose control of the
three aspects of consciousness entanglement. We can create versions of
ourselves in other places, spaces, and times. This is our legacy as
multidimensional and multi-functional beings. We can adapt form to
communicate with other places, spaces, and species. Sovereignty is
earned when the soul can leave at will. DNA was designed so when we
reach a certain frequency we are no longer solely within chemical
experience. Chemical exchanges are fundamental to the life forms living
in this third density. Our journey is from chemical to light. The water
--- the fluids --- that comprise the atoms of our bodies become a
resonant amplifier. Light based experiences happen through the
refraction of water. The soul is the light inside the body. The water
and fluid are refracting it by chemical reaction. When you shine light
through water or a prism there is no chemical separation of the prism of
light. Thoughts can be implicate and explicate at the same time ---
orgasmic experiences, love, and fundamental experience without thought.

Reincarnation was a trap that created karmic entanglements. To get back
to celestial mediumship, reincarnations are optional and free willed for
karmic resolution. We achieve multidimensional living and realize
leaving here was never truly the goal. Multidimensional existence is the
goal. We can generate a part of ourselves that continues the journey
while having many other parts of ourselves in other places. The \emph{I
am} apex presence roots uncontested in the here and now. Reincarnation
and some forms of incarnation became competitive reduction journeys. The
entire experience of death is set to change. Our lives will go to three
hundred years, five hundred, seven hundred years in one go. The passing
over experience will persist to finish this era of light's karmic
accounts. Our capacity to plan future lives with twenty to thirty
percent of our life memories, hundreds of millions of years as our
database for mapping future lives.

At the moment we all have to grow up very fast and our \emph{I am}
technology has to come out quickly in our body. That's because we are
not put on our mother's heart for days after birth with the umbilical
cord still connected. We will have more natural birthing with pregnancy
going from 9 months to 25 months. Everything is going to slow down
versus our fight flight adrenal gland living that we are having now.
There are children here now with a good part of their memory available
to them. They might be ahead of time but lack their parents' guidance on
how to deal with it. The fetus in the womb planning will totally change
too. The mother and father will be a part of the planning journey even
before the fetus enters the womb. No more accidental pregnancy as the
women will have enough control over their eggs and the men enough
control over their seed to not allow connection without creating damage
in the woman's body.

Q: How many more incarnations are we talking to get to this place? It is
not a numerical journey as it involves the understanding of time and
no-time in the 4th dimension and multiple bodies. It is tough to say
this is my last incarnation because what about the person that died
yesterday who said fuck it \emph{I am} coming right back in or the
person that dies next week saying he is not coming back until after the
awakening.

Think of 13-19 \% of our population having enough control over the
Sympathetic and the Parasympathetic. The vagus nerve can begin using its
multidimensional legacy leading us to having offspring with the
multidimensional legacy embedded into their upbringing and culture. It
is not a numerical version and difficult to predict at this stage. It is
really that in the 2050s that culture will have probably sufficiently
changed to have offworld beings come and go and live on our surface
without restrictions. Just like people were saying 2020 felt like a
decade. 2021 will feel like 20 years with all the upheaval and
revelations packed inside it. The nature of time is allowing a denser
basis of experiences. How much light we can carry and retain as memories
will determine how fast the awakening is potentially occurring for every
individual on their unique journey.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  SPACIAL AWARENESS generated in the incarnate life form.
\end{enumerate}

Q: How does movement impact on our bodies and consciousness? PHYSICAL
MOVEMENT is one of the ways where we, as the \emph{I am} instrument of
experience, entangle with individual consciousness as well as with the
collective consciousness, going back and forth from explicate to
implicate. As we change our environment and literally move through
different levels of consciousness we alter the existing as well as our
consciousness is impacted by the fluctuating fields of electromagnetic
energy. Depending on the positive and negative charges of the
surrounding energetic environmental impulses and signals the body's
cells are continuously changing and adapting, seeking harmony. In
epigenetics they found that our genes are made up of 50\% DNA and 50\%
protein. Genes are not self-actualising which means they do not control
their own activity. They form a blueprint, DNA programs for its own
reproduction, that does not turn on and off. The part of the proteins
comprises the structure of the human body creating shape and influencing
human behaviour through the ongoing attempt of balancing charge and
polarity from the environment.

Our individual bubble of reality gets enriched in experience and memory
through the journey on the celestial neuropathway process, taking us
from locality to locality, from one hologram to another expanding the
Orchestra of Consciousness. The neuropathways are an assemblance of
proteins that move the body and help it to function. We all know how to
walk through this reality. This is your invitation to look at it from a
consciousness perspective and acknowledge the influence of each and
every environment on our physical, emotional and spiritual wellbeing.
The Celestial mind generates a hologram in which our DNA instrument can
have experiences, playing from the sheet music the orchestra is using.
All living consciousness is part of the orchestra. Their individual
instruments determine what group of culture, soul families they are born
into. We are all playing from the same celestial orchestra sheet music
but we don't always hear the rest of the orchestra. We only hear our
solos and the instruments that match our signature frequency through
frequency, vibration and harmony.

As we go from our house to our car we have changed localities and
harmony frequency vibration that is taking us onto a road that is more
intra connected to the celestial mind because roads are karmic
transference and resolution points. All car accidents are karmically
created, no coincidences there. When people are driving, the Sympathetic
and the Parasympathetic are in a form of agreement so that the fight,
light or freeze does not take over and create excessive fear to create
accidents. Driving is an experience that allows more instruments to be
aware of each other, a way of connecting. Using the musical metaphor we
are closer to other instruments and tones, the birds, the bees, the
ducks, other cars, the pavements, telephone wires carry consciousness
back and forth, we are in the meaty part of the hologram.

Q: How does this relate to the BUBBLE OF REALITY? Our individual car is
our own tune going from locality to locality via the journey of
frequency, vibration and harmony. Most of the time we get in the car we
know where we are going but not always. Our FVH from the time we leave
the house and get into the car will know the FVH match of our
destination even if we have never been there before. It is part of the
background consciousness of the planet or the maestro that is directing
us from point to point through universal synchronistic blueprints. As
the body moves through the holograms the experience is filled with more
energy and we reciprocate with our energy. We are energy in motion,
chemical and energy bodies at the same time moving through the hologram.

Q: What holograms are impacting on our individual hologram through the
movement of our bodies? CULTURE which binds us to an era of history. Our
culture has Roman Numeral Time which is not our true accurate time
stamp. It may use elements of it though because our culture binds us to
an era of history which is part of the hologram of resolution. Our
entanglement into the culture's hologram of roman numeral time builds up
a weave into the individual hologram. We are reaching a point where many
more instruments are playing.

WEATHER is also an intricate part of our history, part of what is going
on at the time. Weather is also intra connected to programmed water. The
programmed water of an era of history determines our weather patterns.
We as human beings are constantly imprinting on the water on an
uncollective level to create a collective.

ANIMALS \& PLANTS as conscious beings of choice, even though they
haven't been given the rights, duties and responsibilities as beings of
awareness to experience love. Our laws don't include them as part of
that. The rest of the network of life and our laws are separate from
that through conscious entanglement with the narrative. Trees,
plants\ldots{}. anything that has consciousness and experiences life as
part of the planet. Our journey into the great awakening is knowing the
network that is out there. We are responsible not to step on the
journeys of all the other things living here. As part of the great
awakening the ducks, the dolphins, the whales, all of them are part of
the awakening too. It is not just solely for us humans.

CRYSTALS, ROCKS are communities of beings that are part of it too. We
don't have conscious awareness on how they interact with us even though
it is our birth right and legacy of daily living. CRYSTALS ARE part of
the implicate/explicate order as they are SIMULTANEOUSLY entangled and
unentangled. We can imprint upon crystals , entangled narrative
perceptions and agendas with our precognitive workforce. A crystal will
do what it needs to do for us based off how our precognitive workforce
manifest the matter. They are part of the ocean of awareness that
becomes part of the sea of consciousness as animated matter. The crystal
allows you access to the ocean of awareness, the sea of consciousness
based off your capacity to perceive, receive, process and manifest it.
The crystalline structure is materialised, no longer a fluid Ocean of
Awareness or Sea of Consciousness. When we enter 6th and 7th dimensions
crystallisation is the lower end technology of generating matter based
awareness.

FAIRIES: The things that are sightly out of phase with humanity, the
fairy kingdom, the dwarfs and gnomes even though we can't see them with
our eyes, they are still here and layered into the reality. The SUN is
what creates the fundamentals of time, the passing of the seasons and
the movement of the stars. Roman Numeral time has tried to hijack our
awareness of that to make it centric focus of its resolution. At places
of power that we are naturally attracted to, where the veil between the
layers of reality becomes thinner, it is easier for our consciousness to
have more capacity to perceive, receive, understand and interact with.
