\subsection{Agencies}\label{agencies}

We use \emph{I am} agencies here as a metaphor to explain the subject
matter. Agencies are made from energies of existences outside of time
and the \emph{I am}. The \emph{I am} is finite in time. Those energies
still entangle us in this lifetime. Those agencies are not always
operating at the highest standards and practices comparable to the
precognitive workforce. We can have a contract resolvable only in high
frequency. We have to work with low quality agencies to resolve karma.
We can terminate cooperation with an agency and agents outside agencies.
Culture is an external factor that influences the themes of agencies and
agents. For example, the agency is our first point of contact when we
are a fetus in the womb. Together with our higher self it is responsible
for creating all spiritual contracts for this lifetime. The employer of
the agency is is, the human, the \emph{I am} of this lifetime. The
employees --- agents of the agency --- are the various pre \emph{I ams}
who represent the many expressions of us in the unseen. They don't
always work in unison and sometimes try to take over the agency. The us
of today was once a fetus in our mother's womb. The fetus knows it needs
a variety of experiences to plan infinite potentials. It works hand in
hand with the agency to make a series of contracts which fit our karmic
resolution.

It's possible another fetus in another womb is you as well. Our soul is
far too big to just fit into one DNA body. Simultaneous bodies as part
of our soul expression is common. The more efficient the agency works,
the more often we reuse it through our many fetus plans. Some of them
are low quality agencies. They can mess up the matching of our \emph{I
am}. Often an agent has worked with several other \emph{I ams} and has a
good working relationship and reputation.

The fetus comes through the birthing canal and enters the great
forgetting. The child starts unfolding its own awareness around two
years old. It's no longer directly working with the first point of
contact in the agency alone. The \emph{I am} baby is settling into the
new DNA skinsuit and is learning from the parents and the environment.
As babies we have full access to the vagus nerve which means we are
still connected to the mystical side of this existence at a larger
level.

The vagus nerve is like a control room. It operates the body with its
special skills. The \emph{I am} is housed in the vagus nerve with access
to the entire consciousness DNA experience machine. As the \emph{I am}
gets older, it works with different levels of authority within the
agency. Often at puberty the \emph{I am} fires the existing agency. Why?
The \emph{I am} says: \emph{I have to be a sovereign being in this
lifetime and as such I need to take back my sovereignty from all these I
ams represented by the agencies}. Most of it happens subconsciously. The
level of hormones drive us during puberty. The \emph{I am} apex presence
here and now has the power to boot out other \emph{I ams} if they are
trying to run the agenda through the \emph{I am} apex by corrupt
agencies or soul families. Agencies can also be shared by soul families.

A bankrupt \emph{I am} is someone who gave up the responsibility of
creating their reality. They handed over authority to the programs and
former \emph{I ams}. It could be a person in a post life review who
chose not to cross over right away and hung around as a temporary ghost.
This creates a longer form of shadowing and fractalized soul shards.
When finally crossing over the \emph{I am} no longer has a point of
contact to assist with the life review and future fetus planning. There
are times when a living person has become a bankrupt \emph{I am} or has
given all authority away.

The \emph{I am} apex has the power to out-create itself. An \emph{I am}
at any point can go into the vagus nerve and begin the journey of self-
mastery, self-healing, self-nurturing, and kick out the negative
programs that are in there. There are times when we give authority to a
protective part of us, a program, a self-created demon. It takes the
authority. It says, \emph{I get to work with the agencies you don't}. It
doesn't give us any indication, no memo or email. When bad things happen
in our lives we are usually not in our \emph{I am}. We're not fully in
our body and vagus nerve. They're not in the driver seat. False
synchronicities can be created when an \emph{I am} has too many soul
shards in them. The soul shards begin to take over the \emph{I am} spot
in the vagus nerve. They contract with the actual agency in unawareness
of the \emph{I am} that has made the original contracts. In order to
step back into the mighty \emph{I am} apex it takes daily practice,
courage, and determination. We must continue the work of self-mastery
without the neediness of instant gratification and external validation.

Agencies can work in multiple time-space equations. Agents inside the
agency are certified to work in time and no time. Some agents work with
other non-certified agents of other time-space equations for the purpose
of forcing a match no matter how minute it is. Agents and the agency are
separate entities. Think of them as independent contractors who are
contracted by an agency to do the work. Some agents are full time
employees and some are outsourced contractors, akin to when a bank sells
a product and bets against what they're selling you. Even though the
\emph{karmic resolution machine} has run its course, we as beings are
still attempting to reincorporate our fractured selves, our traumatized
and charged perspectives. This allows the agencies to use those
traumatic experiences as a perspective for matching us to let go of
karma and work towards dharma.

The agencies contracted out in the womb are still working with us in the
now. As long as domination and control still exist, where we are forced
to accept tens of millions of layers seen and unseen, we will be dealing
with agencies and contracted agents of agencies who have three degrees
of separation from the responsibility of the destruction they cause for
someone who is not equal to the level of awareness during this time of
awakening.

The \emph{I ams} working against us can be resolved with contract
revocations, shamanic work, and daily practice of self-mastery. We all
have parts of us that work for the domination and control agency. We
have \emph{I ams} that work for thousands of different agencies
throughout the universe. High level shamanic work is getting rid of the
one star agencies to only start working with the five star agencies. Low
level agencies have a very low standard of signature frequency match.
Higher quality agencies have higher standards of match making. The
agency is here to help you write a contract on the fly. That is best
resolution for all sides. Low level agencies look for lower levels of
resolution to get their quota.

The vagus nerve is the universe in realized potential. The \emph{I am}
must learn to drive the vagus nerve like a race car driver. The Schumann
resonance is the speed limit sign or no speed limit sign. The agencies
like to give us speeding tickets without authority to slow us down.
There are construction zones where the \emph{I am} sets up a building
phase and at times the \emph{I am} creates a rebel who screws up the
plans. This is when traumas take over life planning. The fetus gets shut
out of this part and tries to get itself back into trust with the
\emph{I am}. These are the blame, shame, guilt, fear agents that
exponentially get worse with age. Faith is a key component to
understanding the levels of separation. Loss of faith and trust is loss
of control of the vagus nerve. Once we lose control of the vagus nerve
we are in a self-made crisis ruled by hesitation and doubt. When there
is no coherence between mind-heart-spirit, there cannot be a resonance
to the seen and unseen world that is trying to align synchronicities to
us without us being paranoid about them. We start attracting low quality
agencies and the Schumann resonance is there to determine how powerful
and potent we can be throughout an era or slice of history. It is only
the agencies or self-created internal programs that put out the speed
limit signs. The highway goes in every direction but we still have to
guide ourselves with confidence from point A to point B, which is
resolution of conscious awareness at the level of responsibility as an
\emph{I am} of someone who is fully realized in the vagus nerve on the
super highway of the self. The speed limits can be seen as programs that
need to be taken out or considered as data and input to learn and
evolve. Conspiracy theory is an example of speed limits to slow us down.
The system of domination and control is a low level agency. Agencies
have different levels of practices and standards.

Let's say we want to go into spirituality and not do the nine to five
work life. We deliberately put in a constructions zone to limit the
speed of any programs that may want to take us off that path. It is how
the \emph{I am} sets up discipline of the self. In the eastern spiritual
paths they say our lives are written before we are born. It's true. They
are \emph{outlined}. Our free will decisions inform the outcome of the
blueprint. In classical Greek thought we have the notion of fate and
destiny, a reiteration of the eastern adage of the life outlined before
birth. When you look around it's everywhere. Our journey to
self-illuminated master means we can't let our programs influence us to
make hasty choices that don't work in our long term favor. Programs
bring up a subject matter. They have charge and polarity behind them.
When we give into them the program in the vagus nerve is running us and
not the \emph{I am}. The pre-planned construction zones are all about
frequency, vibration, and harmony. They aren't necessarily a bad thing.
They're here to help you on the path. There are deconstructions zones
where a person has had lifelong trauma and needs to stop the traffic,
completely tear up the roads, and create a detour so that there is only
one new neural pathway from which to choose.

Agencies will look for how present you really are so they can match us
with a being of similar resonance to our time-space equation. This is
what we can call time syncing. Once you are in time sync with an agency
it can contract for you --- people, places, things, objects, art pieces,
anything that can create an experience which manifests a memory with
lasting expressions. Astrology has a big part in how the agencies can
work with us. It builds on what sticks in light memory or trauma memory
and from there a blueprint is formed. The system of domination looks to
predict us the same way and tries to get us to work with its corrupt
agency.

A spiritual strategy is an agenda in your time-space equation so that
things can naturally time sync with you and you are not forcing them.
Often people can't find their perfect mate because they are trying to
force matches. It's a pure energetic thing that does not have a
cognitive function behind it. The purpose of the \emph{I am} is to
cognizize things in a time-space vocation, to have access to its vagus
nerve, equal to its level of awareness so a series of experiences can
transcend chemical memories. Those chemical memories become powerful
light memories that allow us to remember things about us during the
great awakening that is part of ascension into higher states of being
while still present in this world that has all these incoherent factors
to them.

\subsection{Entities and Demons}\label{entities-and-demons}

A program may or may not be consciously entangled. It all depends on how
life force empowered the program is. The more we are out of our body,
letting the program run us, the more it's entangled with our vagus
nerve. The vagus nerve gives it access to our special skills. It creates
confusion about what is the soul and what is the program. Some people's
bodies are controlled and run by programs. They take over the vagus
nerve. The \emph{I am} is unaware. Once programs take over the we are
susceptible to entity association. Entities can take over the programs.
Karma determines the growth and veracity of actions entities take when
they take over programs. Entities might not know they're being run by
karma. It is easy to get lost between what is internally created and
what is external entities.

Ninety-nine percent of entities are self-created. One percent is
bonafide haunting. Not everyone is meant to work with entities. There's
an intuitive factor to knowing what to work with. If we don't have the
intuitive factor built in we should not be in that realm. It's curiosity
learning. It happens when we let the programs run us. When we are
curious about something we are not the neutral observer. Curiosity
itself has a charge and polarity. We are controlling a subject matter.
It's right at the edge of the unknown. The brain fills in the unknown
before it's known. People want to know and are falsely drawn to it by
paranoia. It's a vibration in them saying, \emph{I need to know about
entities so they don't invade me}. They might not have had any around
for months, but the curiosity draws them.

There are certain forms of energy we might confuse as an entity. They're
just shards of us. They initially were part of the story we created,
then they turned into internal programs when the story was empowered by
charge and polarity. A trauma can develop from a scary story. It doesn't
really affect us or turn into full blown fear, anxiety, or paranoia. We
can go back to the original story we over-created, see the tree of
creation for what it really is, and release the trauma. A lot of people
need help to get back to that source. Not everyone can do it on their
own. Certain people with ancestral DNA switches turned on don't have the
capacity for that self-inquiry.

There are times when the story is so strong the entity takes over the
life-force and the person finds it impossible to disentangle. As healers
we have to slow down. We shouldn't go beyond the match of our vibration.
The house always wins. You never know what's next when people are
possessed. We are the alpha entity, but self-defeating habit patterns
make our potential a low match to high vibration. Getting out of shame,
blame, and guilt is the beginning of the healing journey.

When we are speak to someone run by an entity we usually talk to both.
We speak to them and the entity simultaneously because the person is
both an entangled and unentangled observer in that scenario. Make the
entity come out to a conversational match so we can speak to it. The
client can be a fully unentangled observer listening to you talking to
the entity even though he or she is using her vocal cords to respond to
its thoughts.

When people work with very low quality agencies to create, they often
use us as a signature frequency match to get others into their web. They
find it difficult to be on their own or need instant gratification and
constant validation for their ideas and creations. As a healer or
teacher we will see that a lot of people falsely match themselves with
you. When we know it is a false match, we can use it to our advantage
and not create karma. Depending on the power of our vibration, if potent
enough, their alter ego has to retreat and their \emph{I am} can feel
the vibration. The altered ego is usually a chicken shit. When the
\emph{I am} has to defend its actions, it shows us how misaligned with
its own sovereignty it really is. We have to maintain a high vibration
not to let chaos define the key notes.

Shattered shards of \emph{I ams} are either bankrupt or fractalized
\emph{I ams} unauthorized to deal with an agency but still take on this
responsibility without our authority. We all come across these forms
during the healing and teaching journey. Take someone who has been
sexually abused at a young age who uses an altered ego to protect
themselves emotionally. Then they go through healing, and they no longer
need that shard, or, they use chemical drugs and create more shards,
demons, vigilantes falsely protecting them.

An external demon is a life force that has not crossed over. It
maintains itself as a surface bound energy spirit, draining life force
from others. It cannot produce its own light. It could be an \emph{I am}
that didn't want to pass over, or an off-world being that could live
thousands of years but lost its capacity to maintain a single body. Its
\emph{I am} can create new bodies temporarily, but the vibration of this
world doesn't allow these bodies to stay in existence long. This is why
it possesses other bodies.

An internal demon is the result of intense trauma. The story becomes so
big that the character goes into the vagus nerve and the subconscious
empowers it to be the potent being, then it becomes the dictator,
tyrant, and abuser through addictions, self-defeating habits, and
self-sabotaging mutilations. The person's internal demons try to
dominate and control the external demons. External demons often run as
the internal demons can be very strong and destructive.

An implanted entity is a powerful demon that has thousands of ways
harvesting energies off you. They control many minion demons much
younger under their hierarchy. It's well documented in CS Lewis's
\emph{The Screwtape Letters}. It will implant into you, and its job is
to pretend to be your inner higher voice until you won't be able to
distinguish what is your voice and what is the demon's voice.

An explanted entity is something that has been put inside you to create
a signature frequency match and then purposely ripped out to create a
drama. Once outside of you it still vibrates on your frequency, serving
as a bait line to lead you down a track of false synchronicities to
negative external sources.

Inculcated entities are advanced puppetry --- you don't know who or what
is pulling the strings --- a very old external demon source with lines
into thousands of minions feeding up the tree.

A clone has a spark of the person in it. The spark has a similar
spiritual contract pattern to the original being. It's against sovereign
free will rules to collect an entity's DNA and make a clone of it.
Cloning against someone's free will creates a person that is dominated
and controlled with little or no sovereignty. This would enable other
sentients to take over the body at any point. The vast majority of the
worlds trade beings genetically built with a suit for consciousness to
broadcast from one planet to another. That suit can be inhabited for a
period of time and then put into cold storage for later use, or they
unmanifest the body, travel energetically to a planet, and manifest a
body there.

Running into a fully depressed person can be tiring. It's important to
know when you speak to the person or a program, an internal demon. When
the person is in the body, the programs are shut off. Sometimes external
entities can still come in. There are people with powerful external or
internal entities in them who are subjugated. We can hear it in their
voice --- how meek they are. There is no power in their voice.

\subsection{The I Am Individuation
Process}\label{the-i-am-individuation-process}

Time is irreversible. There's is no linearity to it. Energy is
indestructible. Every moment within a time-space equation creates an
energetic imprint that cannot be erased. No two physical objects occupy
space simultaneously. There is no simultaneous or identical history as
they follow a unique light path. We are a standing sine wave of
existence as the \emph{I am} apex in embodiment now, in resonance or
dissonance with our previous and future source streams. The quantum
hologram carries the complete history of each energetic imprint of all
source streams within this time line paradox.

We have mighty \emph{I am} selves in the past where we were an extremely
powerful energy being compared to what we are now. As part of karmic
resolution we gave away our \emph{I am} self sovereignty to conduct
timeline recovery operations. Those ancient \emph{I ams} plus another
forty to fifty \emph{I am} selves spread all over timelines and
dimensions are still making decisions that can alter our present
choices. This is one reason why so many people are unsuccessful in this
present world. When we have two or more present selves making choices in
a free will universe. One choice contradicts the other. We cancel
ourselves out at the co-creator level. There is another level of paradox
in which we have one present self on a high energy earth, and another
present self on a very low energy earth. One can easily dominate from
high or low energy. Reclaiming our sovereignty reclaims our authority
from all high energy versions of ourselves in competition and hierarchy.
It removes our citizenship from all involved organizations. All our
shards, parts, and avatars can leapfrog forward in time and claim unity
consciousness to remedy all paradoxes.

When we transit timelines we must figure out which is the optimal for
us. It can also be involuntary. We could call this a form of harvesting.
We can get deliberately thrown off our timeline, or we can have chunks
taken out of us and put into different timelines. This sounds fanciful,
but remember, our DNA is technology. Entire ancestral lineages are being
harvested like this for eons of time.

A point comes when the harvesting ends. We must make a final choice to
be here and now with our friends and family. A scenario like this would
be planned pre-birth. It is often facilitated through a traumatic
experience in this lifetime. It gets us to the time line we need to be
on. A good way of working through such traumas and dramas is to look at
a photo album. Get in touch with the us at the various stages of our
lives. Bring memories to the surface and look for pattern recognition.
People are often born onto the wrong timeline. The soul knows it. It has
to go through trials and tribulations to get back to where it needs to
be. The dreaming body --- the main time traveling technology for us ---
facilitates those changes.

The mighty \emph{I am} apex presence co-creating self has come into this
world now as a representation of all our sentient selves which
incarnated into this world before with decision making power for all the
celestial minds of our past, present, and future lives. Only the ever
present mighty \emph{I am} self in the now can make choices in
co-creation with the unity consciousness world. In other words the
\emph{I am} apex presence of the now is the ultimate choice mechanism of
this lifetime. Other aspects of our self can provide the information
upon which we make choices. The ever presence is literally all of our
other selves in dominion with the \emph{I am} presence now resolving
contracts with soul family, soul planets, or whatever else we are
experiencing in this reality. We, as the \emph{I am} apex presence, are
deeply honored by all the ancestors because we are in an ongoing
co-creation with the world to expand consciousness as a global community
of transformers and consciousness explorers.

The essence of this universe is free will of the \emph{I am} presence
now. The soul and higher self are included but the higher self does not
get to make choices only the \emph{I am} presence does here and now. The
higher self can counsel but it can't give us the questions, only the
answers. When our history is eliminated it puts us in the paradox of
paradoxes. We don't understand who we truly are. We may not even have
any questions to ask. This is often an indication that there are parts
of ourselves making decisions for us without us involved. Those
paradoxes can be forty or fifty \emph{I ams} at the time working on
destruction rather evolution. We can't destroy other \emph{I ams} but we
can work with them. We can heal them or we can ban them through our free
will choices and actions within the authority as this \emph{I am} apex
presence of the now.

We are already the higher self. The \emph{I am} is here in time, as
constructed by the higher self during womb planning, and the higher self
is holographically interacting with you at all times. The \emph{I am}
here and now is based off several previous \emph{I am} selves who have
gone through life reviews and set up a theme of karma or dharma for this
lifetime. In the first five years or so we fully activate our \emph{I
am} technology. The rest of the \emph{I am} comes in during puberty. Our
higher self remains the sacred neutral observer throughout all our
incarnations. When we die we meet our higher self again as ten thousand
past and future generations of other selves. The \emph{I am} is the
technology of interface with the god source already in us. We have to
learn to get to know ourselves as the embodied spiritual human to
understand our soul's purpose and missions.

\subsection{Schumann Resonance}\label{schumann-resonance}

The Schumann resonance is the background frequency of electromagnetics
that is effected by solar winds and radiation, the actual magnetics of
the planet. It represents an opportunity for consciousness to rapidly
expand. If you feel that you respond to the spikes it might say to you
that you have all this electromagnetic thinking juice and you are not
doing anything with it. The Schumann resonance is not one number. It's
many, like a team dance combination. There is no one common shared
Schumann resonance around the world. All of them make up the orchestra
of consciousness. Mountains, lakes, deserts, and rivers alter the
Schumann resonance. The seen and unseen life in those areas affects it.
Think of the Schumann resonance as the key in which musicians play.
Through consciousness we are quantumly entangling with the Schumann
resonance. Working with our \emph{I am} agencies is a choice in
awareness, unawareness, or both.

The Schumann resonance determines the veracity of interaction. It's the
key that allows things to act in synchronicity so that best matching
actions create powerful manifestations. The quality of the agency
determines the power level and the time of action in a key. The Schumann
resonance is there to keep all living things seen and unseen on one
celestial musical key. Free will allows us to explore many keys. We can
create resonance with the natural way of living or we can create
dissonance. A dissonant state is the cacophony of chaos, which is its
own universal key.
