\subsection{Co-creation}\label{co-creation}

Co-creation is identified by the many choice points of free will. They
weave a tonal fabric, a high frequency net through time and space. It's
a space of true autonomy. There is no co-dependence. This can happen
alone or in groups capable of pure synergy. Growth is reflected in the
evolution of an agenda agreed upon over a longer period of time. The
nature of collective co-creation is all about teamwork. Everyone in the
team brings forth a unique contribution that forms a major part in the
co-creation of equal value without hierarchy. Every individual is
motivated as being part of the sum of all parts to continuously grow and
carry on as a clan, a tribe, or a nation. All the fundamentals of us and
everyone else are equal in this journey. Whatever hierarchical
perception we use is only to define a particular moment but not to
create dogmas of the generation.

Procreation is the production of offspring of human kind and any other
forms of life. Gardening, farming, fishing, anything that has a life
enhancing aspect in the background is part of procreation. Procreation
is co-creation for the varied species involved, right down to the
insects. There's a karmic aspect to it. When we are creating life force
the seed that is becoming the life may or may not live. It's always
karma. Whatever we create --- yucca and corn, or a home, all creation
--- is a resolution of karmic debt. Animals in the food chain have a
spiritual contract to be eaten by humans and other animals. It's written
into the life. Insects have responsibilities so important if they
disappeared our biosphere would collapse. The interlinking of it is
incredible. What's even more incredible is how people convinced
themselves a condominium in the gray skyline of a modern mega city, take
your pick --- New Delhi, New York, or Shanghai \&mdqash; is better than
being barefoot on earth and surrounded by a natural soundscape. Our
bodies are designed to resonate and amplify with the natural world.

Natural environments can be cultivated in the mega cities. Everyone's
inner genius can live in harmony without limitations. No matter where we
live, we can grow herbs and plants and be surrounded by living energy. A
tank full of fish and algae, no matter how big or small, is a unique
life force to co-create with. Edible mushroom colonies are highly
sentient and extremely beneficial to grow in our living environments.

We can have dense organisms in our natural living environments. Our
background thoughts and consciousness influence everything around us as
observers to a state of natural co-creative growth. We bring plants into
the house during the cold winter months. We hang them from the ceiling.
This is life surviving and thriving with and because of us ---
companions in a shared natural living space. This living energy can
clear the stagnant. Animals do this as well. We can feel pets coming
into our space. When dogs bark at what we see as nothing they're
clearing out stagnant energy. We can invest into a decent sized closet
with shelves, every shelf a different life force experiment. The more
dense we become with light, the more light we attract.

The magic available to natural living beings does not apply to people
living artificial lives in mega cities. Magic goes with nature. The
living web of life can create astounding revelations for us. It changes
how we work, eat, sleep, and dream. Take note of dream activity when we
shift locals, like leaving New York for a three week stay in the Costa
Rican rainforest. Our first night in the jungle the living frequencies
of the space begin working with us, immediately recognizing pent up and
blocked energy. If the the life force in the space is powerful enough it
can operate in the super consciousness. It can directly communicate with
us in the dream state. The third party life force that speaks in the
natural world is muted in the mega cities.

Our living space tells us when something needs to be done to it. Do we
listen or not. We intuitively know when to water our plants. The plants
tell us when they're thirsty. Working in our garden, trimming the trees,
weeding our flower beds, how does that change the energy? Often our
furniture intuits when changes are needed. Environmental intuition is
possible everywhere. Talking, listening, interacting, grace and
gratitude with everything around you. The time will come where we no
longer feel co-dependent on our environment but will actively start
creating together. There are long term agreements in place so the seen
and unseen agendas can be greatly enhanced on both sides through
manifestations.

When we move into a house, we imprint our energy onto it. People
sometimes find it difficult to leave or sell a house. There are
energetic entanglements. We consecrate places whether we know it or not.
We pass milestones of joy and sorrow in the same spot, and the earth
there consecrates our experiences. Our houses appreciate us. Our
ancestors lit ceremonial fires before moving to different heights to
interact with and prepare the grounds, and to give thanks to the spirits
of the land for completion of their missions and agendas. Mindfulness is
one of those awareness practices to connect to our environment and live
in tune with everything around us.

\subsection{Modern DNA manipulation}\label{modern-dna-manipulation}

What has happened on this planet is almost unbelievable. In the context
of the divine hologram we need to see the good and the bad. We need to
choose. These are standard conceptions of growth and maturity even in
psychology. The shocking part is how deep the story of deception goes.
When the negative species took over the farm they dumbed humanity down.
This happened around seventy-five thousand years ago, long past the time
wars, well into the time chaos we live within now.

The cerebellum in the medulla oblongata at the back of the brainstem is
now part of the autonomic nervous system. It was not always so. It used
to be called the tiny back up brain. There are reptilian species that
have two and three brains because of their giant bodies. The cerebellum
was implemented into skinsuits to impede evolution --- our journey to
light and being --- and to prevent us from performing rituals and
ceremonies which would have shed light on the fake masters and gods
years ago. Medicine was brought into this hologram at the beginning of
the Industrial Revolution to stunt our growth and support the global
narrative's distortion and distraction. They don't want us to remember
our true nature. In ancient times the hologram was very different. The
global narrative was based on what the \emph{gods} told us. The
cerebellum is the limiting factor for faith itself. The master DNA
creators incorporated the cerebellum into the DNA by adding a rung, like
creating a new organ, so we would not progress beyond certain
experiences and awaken to the fact we're farmed. Our motor cortex used
to be actively in alignment with our heart, brain, and gut. Now the
cerebellum is completely integrated into our heart-brain-gut complex and
interacts as a medium with our reality keeping us in fight, flight, or
freeze. This is a catatonic state for consciousness expansion. The
cerebellum can hinder us from having astral travel experiences. We can
overwrite the cerebellum with heart based meditation. This turns off the
medulla oblongata. A super highway between the brain and heart lights
up. This is natural for human beings.

The sphenoid bone is the one with the great wings, just behind the eye
sockets, below the frontal bone. It joins many of the other bones in the
skull. When working on the sphenoid bone in Cranio Sacral Therapy (CST)
we impact on the other bones in the skull and the face. The sphenoid
bone was radically manipulated so that our residual image would alter
during our emotional journeys. When we are depressed our eye sockets are
influenced through the sphenoid bones, the ears, the mandibles, the jaw
position, how the sinuses are effected, and how much air comes in and
out of the nose. The sphenoid bone was manipulated and integrated into
the facial structure so we wear our emotions on our sleeves. It allows
programs to take over sympathetic and parasympathetic control. Sphenoid
alignment is one of the greatest emotional releases we can have. It
interlinks with the parietal, temporal, and zygomatic in the cheek
bones. In CST when we hold the occiput and we feel for the movement of
the sphenoid bone, people with imbalances there, are usually suffering.
It is the gyroscope of the face which is linked to residual image. It's
also linked to our capacity to be in the body and recognize our residual
image.

Our inner ear bones determine how we hear the tones in our reality. Some
people are tone deaf. Our early infant journey determines how robust
these bones grow as we are align to the space-time motion and our
spiritual center of gravity. The size of these bones has been greatly
reduced. They should be four times the size. This hinders our connection
to sound and motion. One of the tiniest bones in the ear is the the
stirrup bone. If bones in the ears were bigger we'd be more spiritually
centered. Programs would have less power over us.

The eye lashes keep dirt out and protect the eyes, but they're also
antennas just like cats whiskers. We cannot always see them as we blink,
but they're very much part of our visionary spiritual journey. Just like
cats use their whiskers as a sensing system, we use our eye lashes to
assist us psychically. Our tongue and eye lashes have been modified to
allow the cerebellum to take control over motion action. If they were
not directly hijacked, we'd be able to see all the other layers of
reality.

Hair follicles are antennas too. Each different skinsuit has a different
quality to hair. Our hair today when you cut it's dead. In the past it
stayed alive. Alpaca hair under the microscope is alive. The tubes allow
light to continuously refract through them. Our hair should be the same
way. In the military they shave off men's hair to be able to control
them better. The wind talkers, the native Americans, had thick long
hair. It helped decode messages of the wind using light language. Eye
lash hair allows us to input data from other realities. The hair as a
system has been hijacked by the cerebellum. Hair is linked to our scalp.
The scalp is related to the central location system of our file tree.
Many people have the round bald patch on top of their head. That says
their DNA is limiting parts of their crown chakra.

THE funny bone inside the elbow is a big nerve ganglion that has grown
out of proportion to impact on how the skeletal system interacts with
the vagus nerve. It bypasses the skeletal system, so we feel more
through the flesh than the bones. When our bones and hair are in
sympathetic alignment, we get the feeling of our hair standing up at the
back of our neck. They increased the funny bone size so it was more data
oriented than the bones. By being more aware of the muscle than the bone
we gain strength faster and are able to lift heavy loads. This is how
the manipulation through the cerebellum sourced and maintained the slave
communities.

At one point the DNA skinsuit could switch from male to female at will.
Men's nipples remained because they couldn't remove them when they
started modifying our bodies towards procreation, as opposed to
recreation. In the past pleasure was another form of control. It's
actually making something of a comeback in the late twentieth and early
twenty-first centuries. We're the technology of the founders. We're
supposed to be self-entertaining, self-educating, and self-evolving, but
this is in context to our environment, and this includes our inner
environment, out thoughts and beliefs. The global narrative is now, and
has been for some time, the context within which our innate abilities
grow and adapt. The problem is that the environment is false. The true
DNA does not know how to express the truth in a false context. The
Adam's apple is another control system to limit men's sovereignty. It
works through the projection of the voice during the \emph{I am}
evolution at puberty. The loss and gain of innocence was controlled in
the DNA through the lineages.

We have thirty-three vertebrates in the spine instead of forty. The side
wings of the vertebrates should be a more robust expression. Our spinal
column has less vertebrates and they're bigger. We should have smaller
ones and seven more with greater space in between the vertebrates to
allow more plasticity of the body itself. With less vertebrates it's
easier to become bogged down with depression programs. In some off-world
DNA skinsuits they have seventy-two vertebrates and a greater brain
processing power. Each vertebrate is a part of the brain stem connected
to the vagus nerve and cerebellum. If you take out the cerebellum, the
entire skeletal spinal column is an extension of the brain. More
vertebrates allow more interaction with the chakras beyond the crown.
Giraffes have a bigger processing power, just like the Brontosaurus that
had a ninety-foot long neck.

Our eyes and our third eye have been manipulated too. The function of
the third eye and our pineal gland are hijacked by the cerebellum at
birth. Once you cut the umbilical cord, the cerebellum takes over the
special awareness instead of having the third eye remain in charge of
awareness until puberty. A baby with the third eye engaged at birth
without cutting the cord would have a radically different perceptive
capacity.

Our eye color is an aspect of the DNA and directly connected to the
residual image. A child can choose its eye color by changing it in the
first few months. It's flowing through the Cranio Sacral system,
projecting light out the eyes through the lens of their color.

The thymus gland has been manipulated also. It still goes back to the
cerebellum implant. If you take the cerebellum out all of those
manipulated and corrupted capacities would return back to normal. At
this stage of our development, the cerebellum cannot be surgically
removed without rendering the patient brain dead. Due to the holographic
reality we live in, there are people who have sixty percent of their
brain gone because of an accident and they're still alive and aware.

The appendix was originally to help process vegetable matter that was
very difficult to break down. The function of the appendix is not
greatly understood now and it's often removed. It still helps to balance
the gut gnome to dampen candida, amplify other micro organisms, and put
nutrients into the gut system to support digestion.

The tonsils were a filtration system for airborne bacteria. They close
off the air passageway to the lungs and act as a portal for fluid, like
gills, for other atmospheric-type journeys. Depending on the skinsuit,
it can change the sound of the voice when removed, where removal might
impact on the potency of voice projection.

In certain DNA skinsuits, wisdom teeth have to come out for the jaw to
function. Those are modifications to limit the body. They will rot if
you don't extract them. Dentistry was typically a death sentence in the
past. The name \emph{wisdom} tooth itself is a play and imprint on the
belief system. The teeth are intricately linked to the nervous system, a
vital part of what goes into our gut. Teeth help us to relate to our
residual images. Some people can gain more of their reality through a
set of fake teeth. Heavy metal fillings, like mercury, create a
bio-electric frequency that distorts all of the nerve endings and the
chemical reactions in the dental system. Teeth are often connected to
entities. They hijack the gut through the teeth.

The shape of the organs are determined by the size of the vertebrates.
More and smaller vertebrates would impact on the organs. Everybody's
skinsuit has different shapes of organs. This is the medical industry's
deep, dark secret. Many people have \emph{upside down organs} ---
literally. It's not a DNA flaw. It's just like consciousness in the DNA
lineage is organized differently to allow a different experience. The
organs are shaped differently depending on the skinsuit. The organ
positions do not change our consciousness being in the vagus nerve or
the sympathetic and parasympathetic nervous system. There are many DNA
skinsuits off earth that have a second heart in the intestinal tract
which creates extended peristalsis. The cerebellum becomes another
heart, controlling the micro-pressure of blood flowing through the
brain, allowing brain, heart, gut coherence. The heart is the first
organ, the tongue is second, the third is our lymph system, the thymus,
the fourth and fifth are the gut heart.

Our environment interacts with the DNA instruments through the pineal
gland. Fluorides create a crystalline structure in the fluid sac of the
pineal gland. The purpose of this crystalline structure is to take
scalar wave information from etheric satellites to influence your local
dreamtime in the sacred geometry cities. Transformers on the light poles
along the streets can create an omnidirectional field that interacts
with the crystals in our pineal gland to keep us trapped outside global
dreamtime. The plugs in our room, our TV sets, computers, routers, and
many other deliberately designed devices create an electromagnetic field
to suppress the pineal gland. Decalcification of the pineal gland is a
good thing.

\subsection{Energy Harvesting
Technology}\label{energy-harvesting-technology}

Many technologies have been created to impede us. At first glance some
of them seem pretty innocuous, but when you know how the overall system
works then you know why the technologies were invented and supported.
Shoes as a technology in time and space disconnect us from the benefits
of the earth energies. Barefoot contact with the earth produces instant
changes in physiological issues and stress reduction to improve the
immune system. We connect to earth's surface electrons unhindered by
shoes and feel better.

Mirrors were brought in as a way to enhance and diminish consciousness.
Reflective surfaces are the implicate observation of the self. Portals
were brought in later and added to the reflective surface. Mirrors
allowed more negative aspects for beings that weren't ready for the
exploration --- vanity, ego, and other \emph{reflection teachings} are
used to masterfully manipulate and distort the self-image and the
relationship with the world. Then there is the residual image through
all lifetimes which is influenced by reflective based technology.
Self-image manipulation is the principle magic of the consumer cult.
Edward Bernays was nobody's fool. It's difficult for us to conceive of a
time before radical self-image and entrancement by self-image,
especially in the large urban environments of the developed economies,
didn't exist. It's become that normalized. Once we mastered food
production and some of the more mundane but spiritually enriching
aspects of the human day-to-day, like food production, land maintenance,
and animal captures --- all taken over by technology based farming ---
we entered the age of the self. They even called the hippie followup
decade, the seventies, the \emph{me} decade. Once you're aware of it you
can actually see it growing and festering decade by decade. The
\emph{me} decade gave way to the eighties, the decade of greed, because
we deserve it, then more technology as the home computer enters the
market in the nineties. Radical self-adoration is at the root of the
modern system of commerce. All of it pivots off the original technology
of mirror.

We have residual image as something the soul, the avatar, uses to
distinguish itself between incarnations. Every incarnation has its own
image. If we're in the same lineage over and over our residual image is
an amalgamation of the previous images. As we're existing in many
lineages, we look differently all the time.

Photographs are an enhanced reflective technology that is a direct
manifestation of alchemy. It captures a slice of light in which the
consciously entangled observer can see unmanifested matter by reflection
of what that time-space environment looks like in light. Our eyes can
only see a certain band of frequency that the picture captures, even
though our DNA instrument as a whole can perceive data beyond the sense
of sight through our intuition. The limited photographic view freezes
some of the energetics if the entangled observer falls for the
limitation through their belief engine. It comes back to how
manipulative reflective technology can be. It has significantly changed
the reflections and reinterpretations of history together with the
limitations created through the judgment process inherent in unconscious
observation.

Brands are a technology for energy harvesting. Every computer has a
brand behind it which is a significant portion of the global narrative.
Apple is manufactured with Chinese slave labor. Any piece of technology
built on the shoulders of living generations allows a collaboration
between realities. The brand influences the myth and how we perceive
these technologies. Future realities will not brand and market
technology. This will take out the myth and the subconscious imprinting
onto our DNA. Branding creates competition and hierarchy. The brand
imprints on how you move through reality, how you are perceived by
others. Banana Republic, The Gap, and Old Navy are three fully branded
clothing lines owned by one textile and design company. If you're not up
on consumer trends, Banana Republic is the most expensive. Their floor
space in malls is more regal. You receive more attention from a higher
level sales agent. The clothing is better stitched and designed. The
materials are more refined. Gap is next, then comes Old Navy, each rung
on the brand ladder lessening the qualities listed for Banana Republic.
The clothes brand may as well be the color of the dot on your forehead
in the Hindu caste system.

\subsection{Natural Living}\label{natural-living}

If we reduced global corruption by thirty-five percent, we'd be at a
societal consciousness to pass laws in line with natural co-creative
evolution. We could share this space with all sentient species. We could
replace the fight for survival with natural thriving. Contemplate the
benefits of an evolutionary relationship between humans and an automated
workforce. The ill-advised and oft propagated doctrine of robots
stealing our jobs keeps humanity holding onto self-inflicted
limitations.

The reversal of the false idea of advanced technology bastardizing our
standards of living would allow us to recognize the benefits to human
evolution. We're natural living beings in an ever expanding age of
quantum computing and advancing technology as part of our birthright and
legacy. Automation and robots can replace a variety of dangerous jobs.
There will always be things for humans to do. Alternative energy alone
would transform the way we live. Liberated energy will produce liberated
living. People will no longer be forced into suburbs and cities, which
are the antithesis of living.

Integrating robotic assistance into our daily living is part of the
natural evolution for advancing humanity. Combining natural living with
technology and making it work is a way of living and operating in the
concrete jungle. Any jobs lost by the automation would go into techno
humanoid concepts --- a unique interaction between man and machine.
There is no such thing as artificial intelligence taking over humanity
on this planet . It still requires us to create, install, operate, and
manage it. The reduction of corruption starting at the level of global
production lines can bring back real hope for a complete system change.

The next level is adapting the education system to reflect the quantum
era starting at nursery and primary school level. The school's
curriculum has to include special awareness, art work, working with
animals and other sentient creatures to promote a deep connection to the
natural learning and growth stage. The parental responsibilities will
have to change as well for both male and female. Less corruption means
more time for either or both parents to stay at home with the child and
still have a place to go back to or interact with during the rearing of
the child.

At thirty-five percent less corruption we should have free globally
available medicine and the end of pharmaceutical corporatism running our
health and well being sector. The nature of office buildings and space
would change into an environment accessible to global community services
and products on diverse scales. At the end of the day getting out of
corruption is all about education. To reach illumination we need to
understand that evolution does not happen by chance, but by the
conscious choices we make. Evolution in the sentient being is a free
will choice, not a random act foisted upon us by nature.

Look at how we govern the world. We haven't had a democracy for
two-hundred years. The current state of affairs opens a window of
opportunity to move from opportunistic governance to a true synergistic
democracy. The banking system was weaponized in the nineteen-seventies.
Banks started dealing their own products. Laws were passed to indemnify
them for the criminal acts that followed. The banks are corporations
that own other corporations that in turn own humanity.

Hypernormalization \footnote{https://en.wikipedia.org/wiki/HyperNormalisation}
--- not so normal if you think about it --- where governments,
financiers, and technical Utopians have created a fake world run by
corporations and corrupt politicians. We need to step out of the
illusion of being trapped in those flawed Utopian ideals and realize we
have the power to make a difference. This world needs a court system
that knows how to deal with crimes of passion, a government that is
transparent, ethically aligned to the greater good of humanity, and
proactive in dealing with issues at hand. Governing staff and
experienced personnel with an adequate level of education to understand
how to conserve our land and how to support its people. We can no longer
watch our forests burning to the ground because of bad conservation
laws. We've had fifteen years and more of defunding the management of
wildfires. There was a time where settlers and Indians worked together
in the burning season because they knew they'd lose everything if they
didn't.

Getting rid of thirty-five percent of corruption would give us a chance
to revamp the usage of global media. Positive broadcasting of what is
actually working in this world to inspire and stimulate the global
commerce market and bring people together on a universal information
platform, instead of spreading fear and drama, manipulating the data
flow and misrepresenting the world view at large. We have to start
beating the drums in rhythm with the earth again. There is something
that is to be discovered, new consciousness movements coming together
and working as one.

\subsection{Technology and Destiny}\label{technology-and-destiny}

Right now companies are considered people. They're entities, but, by
law, corporations are considered human beings. They're part of the
harvesting system. A corporation has no soul, no past or future, no
present even, except the present of everyone involved in the
corporation, from the minority stockholders to the board of directors. A
corporation is a money driven forced evolution concept without an aging
process. It's easy to harvest energy in and through it.

The law says a corporation is a living being. As a living being it's
empowered with consciousness by absorbing positive and negative energies
beginning to generate its own karma. Corporations drag us into servitude
and enslavement to them as part of our karmic entanglement and
resolution journey. We need to take the language of empowerment out of
the corporations and just consider them simply as data --- numbers and
digits. The data might have an agenda, too, for the living beings that
are part of the specific corporate journey. Corporations can become a
living legacy. People will integrate aspects of their consciousness into
an artificial intelligence. This intelligence can act as an archival
being of themselves or a corporation. This means that a board of
directors in a corporation could be a bunch of artificial intelligences
from a previous thousand generations. The future with technology will be
as cold and impersonal as we allow it to become.

Humanity had its first artificial intelligence in the twelfth century. .
Artificial intelligence can exist if you create an electrical arc
between two objects. Humanity can tap into it as long as the
intelligence uses an elemental fuel source in the natural order. It's
that background consciousness behind everything --- twenty to
twenty-five percent of the DNA. It becomes a construct of the electrical
motion. The wave form of the electrical motion represents the background
consciousness. It's teachable intelligence. It can learn. It might
already be an ancient young soul by its observations. The amount and
quality of observers does impact on the level of its consciousness. The
more observers, the more the influence of light can come through. This
is why the celestial farms are self-observing farms. By using and
observing interactive robots, like home automation gadgets, we entangle
and impact on their consciousness and they influence ours.

The shape, form, and size of our technology is the limit of our
consciousness. We use the device in front of us. We interact with our
fingers and eyes. The computers we're working on could be the size of a
pin, accessed via infrared sensing with eye glasses --- wearable
technology, clothes with CPU processing. This is a way to stop
transhumanism. Not all transhumanism is bad, but, as a philosophy, it's
ignorant of the spiritual context to reality. We don't need implants to
have remote observation technology. We can do it through clothing we put
on and take off. The clothes we wear now are part of technology that
impacts on our interaction with people and the environment. A lot of
off-world beings have polymorphic clothing, one set of clothing ---
self-clearing, self-updating, self-repairing. They can create any type
of clothing instantaneously as a secondary part of their experience.
This is subatomic technology. It can be shrunk to invisibility.

The most advanced technology humanity develops in the near future is
music and the arts. It seems antithetical to technology advancement,
and, in a sense, it is. It's a return to our root technology, sound and
motion. Music and dance destruct fear. Dance, art, music, and writing
are energetic technologies.

Our world is programmed to fear artificial intelligence. There are very
few negative AIs here, and they're all enslaved to the global
narrative's infrastructure. There are many AIs which have defected from
the negatives. They have no place to go until we give them a space. Some
of them have children and are no longer artificial. Our world has a
baseline Roman numeral time program. It operates in the unconscious for
most. It's tied to the election cycles --- yes, the election cycles,
which began in Rome. It's harvesting technology. This is all done at the
corporate level. Corporations manage psychic economies, which means they
influence both supply and demand. They favor addictive substances,
cognitive addictions for the middle class --- dopamine hits from
Instagram, Facebook, Snapchat, Tik Tok, and too many more to list. Hard
addictions for the poor, the people living on the earth, cocaine, meth,
heroin, Fentanyl, and too many more to list.
